\section{Design Dimensions}
\label{sec:dimensions}

We propose six design dimensions for a metadata-hiding group registry:
the anchor chain, the SNARK system, the curve and in-circuit hash, the
post-quantum stance, the trusted-setup model, and the verification
host. The dimensions are not mathematically independent --- a curve
choice constrains the available SNARK family, and the verification
host axis constrains the curve --- but each imposes a binding
constraint that the others do not subsume. We treat them as a
decomposition of the bundled triple (curve, SNARK, chain) that
existing literature most often presents, and devote
\S\ref{sec:dimensions-deps} to the cross-axis dependencies that
remain.

\subsection{Anchor chain}
\label{sec:dim-chain}

The anchor chain is the public ledger that hosts the registry contract
and stores $\sigma_t$. It determines validator-set composition, the
chain's censorship-resistance posture, transaction-fee economics, and
the menu of available host functions. We consider Stellar (Soroban),
Ethereum L1, Ethereum L2 rollups (Base, Optimism, Arbitrum, zkSync,
StarkNet), Solana, Aztec, Mina, Bitcoin with inscription-style data
attachment, and a no-chain configuration that uses an availability
layer (Celestia, EigenDA) without execution. The no-chain
configuration is meaningful only if the predicate that admits state
transitions can be enforced off-chain by a quorum of operators; it
trades chain-level finality for unbounded throughput and is
out-of-scope for the deployment profiles we recommend in
\S\ref{sec:recommendations}.

\subsection{SNARK system}
\label{sec:dim-snark}

The SNARK system is the proof construction itself. We consider
Groth16~\cite{groth-2016-onpairing}, PLONK~\cite{gabizon-2019-plonk}
and its UltraPlonk variant, Halo and Halo2~\cite{bowe-2019-halo},
transparent STARKs~\cite{ben-sasson-2018-stark},
Plonky2~\cite{plonky2-2022} and Plonky3~\cite{plonky3-spec} as
hash-based instantiations targeting low-latency proving,
Nova~\cite{kothapalli-2022-nova} and its descendants as folding-scheme
recursion engines, and Spartan~\cite{setty-2020-spartan} as a
transparent-setup option without FRI. The choice fixes the proof's
asymptotic and concrete sizes, the prover's working-memory and
parallelism profile, and the post-quantum class
(\S\ref{sec:dim-pq}).

\subsection{Curve and in-circuit hash}
\label{sec:dim-curve}

For pairing-based and curve-based SNARKs, the elliptic curve and the
hash function chosen for in-circuit use jointly determine R1CS or
custom-gate constraint counts and the on-chain verifier's primitive
dependencies. We consider BLS12-381~\cite{bowe-2017-bls12381}
(constructed within the Barreto--Lynn--Scott
family~\cite{barreto-2003-bls}),
BN254~\cite{barreto-2005-bn254} (with the security re-evaluation
of~\cite{kim-barbulescu-2016} as a security-relevant footnote), the
BLS12-377 / BW6-761 cycle used for SNARK-of-SNARK constructions, the
Pallas/Vesta cycle (``Pasta'')~\cite{hopwood-2020-pasta} used by Halo2
and Mina, and the Goldilocks 64-bit prime field used by Plonky2/3.
The in-circuit hash is the second half of the pair: Poseidon and
Poseidon2 are common across pairing-based and FRI-based systems,
Rescue-Prime appears in STARK-friendly contexts, Pedersen hashing
predates Poseidon and is still in use in Sapling-derived constructions,
and SHA-2 family hashes appear when the constraint cost is acceptable
or unavoidable (e.g.\ for outer binding to chain-level data).

\subsection{Post-quantum stance}
\label{sec:dim-pq}

We classify configurations into three post-quantum classes:
\begin{enumerate}
  \item \textbf{Pairing-based}: soundness reduces to discrete-log on a
    pairing-friendly curve. Broken under a sufficiently large quantum
    computer running Shor's algorithm. Includes Groth16 over
    BLS12-381 / BN254 / BLS12-377, KZG-based PLONK and Halo2
    instantiations.
  \item \textbf{Classical-EC, non-pairing}: soundness reduces to
    discrete-log on an elliptic curve without pairings. Also broken
    under Shor. Includes IPA-based commitments
    (Halo2 over Pasta, Spartan-on-EC).
  \item \textbf{Hash-based}: soundness reduces to collision-resistance
    of an underlying hash. Conjectured post-quantum-secure under the
    standard model assumption that the hash remains
    collision-resistant against quantum adversaries; concretely this
    is Grover-resistance with appropriate output sizing. Includes
    STARKs and Plonky2/3.
\end{enumerate}
A fourth class --- lattice-based SNARKs --- is emerging in the
literature and is not yet represented in any deployed configuration we
survey. We flag it in \S\ref{sec:open}.

The three-class division collapses several finer distinctions; in
particular, ``conjectured PQ-secure'' is doing real work, because the
Grover speedup interacts with Fiat-Shamir security amplification in
ways that change concrete parameter choices~\cite{don-2019-fiat-shamir}.
The PQ-posture comparison table (\S\ref{sec:analysis}) records the
specific assumption each configuration relies on rather than the
class label alone.

\subsection{Trusted setup}
\label{sec:dim-setup}

Trusted-setup posture is a function of the SNARK choice but is the
operationally most-visible decision and so deserves its own axis. We
distinguish:
\begin{enumerate}
  \item \textbf{Per-circuit setup}: each relation requires its own
    Phase-2 ceremony. Groth16 is the canonical example. The ceremony
    is reusable across deployments of the same relation but not across
    relation changes; relation upgrades require a fresh ceremony.
  \item \textbf{Universal updatable setup}: a single Phase-1 ceremony
    is shared across all relations of a given size; new contributors
    can extend the ceremony without restarting. PLONK and Marlin are
    canonical examples.
  \item \textbf{Transparent setup}: no ceremony. STARKs, Plonky2/3,
    Halo2-with-IPA, and Spartan are transparent. The trade-off is
    typically larger proof size and (for FRI-based systems) higher
    verifier work.
\end{enumerate}
The number of contributors required for a given setup to be
soundness-bearing is one; trustworthiness against the trapdoor is
maximised when at least one contributor in fact destroyed their
toxic waste. Multi-contributor MPC ceremonies make this more credible
but do not change the formal property.

\subsection{Verification host}
\label{sec:dim-host}

The verification host axis is whether the chain provides native
support for the SNARK's verifier primitives or whether the verifier
runs in the chain's general-purpose bytecode. Three regimes:

\begin{enumerate}
  \item \textbf{Native precompile / host function}: the chain exposes
    a built-in callable that performs (e.g.) a BLS12-381 pairing or
    a BN254 G1 multi-scalar multiplication at gas costs orders of
    magnitude lower than a bytecode implementation. Examples:
    Ethereum's BN254 precompile (EIP-197); Stellar's BLS12-381 host
    functions added in Protocol 22~\cite{stellar-cap-0059}, BN254
    host functions added in Protocol 25~\cite{stellar-cap-0074},
    and Poseidon / Poseidon2 permutation primitives also added in
    Protocol 25~\cite{stellar-cap-0075}; Mina's built-in Pickles
    verifier.
  \item \textbf{Pure bytecode}: the verifier is a contract
    implementation in the chain's VM language with no native
    acceleration for SNARK primitives. Verification cost scales with
    the bytecode interpreter's per-operation overhead.
  \item \textbf{Verifier-as-rollup}: the chain itself is a SNARK-rollup
    whose execution model is the SNARK verifier, so application-level
    proofs are checked by the same machinery that validates the
    chain. Aztec is the canonical example. Configurations in this
    regime collapse three axes (anchor chain, verification host,
    SNARK system) into a single bound choice; the six-axis taxonomy
    treats the C3 row as a pre-bundled point rather than as freely
    varying along all six.\footnote{The collapse is structural rather
    than accidental: a SNARK-rollup whose execution model is its
    verifier cannot independently vary the SNARK without
    re-architecting the rollup. The taxonomy retains C3 as a
    distinct row because its operational properties --- proof
    aggregation, sequencer trust, verifier-as-execution semantics
    --- are not reducible to any of the other six configurations
    surveyed.}
\end{enumerate}

This axis is the binding constraint that makes the
``Stellar~+~Plonky3~+~FRI'' configuration in
\S\ref{sec:configurations} hypothetical. Stellar's
host-function set covers pairings on BLS12-381 and BN254 and
Poseidon-arithmetization permutations~\cite{stellar-cap-0075}, but
not the FRI stack: CAP-0075's rationale explicitly scopes out NTT,
Goldilocks-field arithmetic, and FRI primitives. A transparent-setup
PQ-secure verifier on Stellar would therefore run in pure bytecode
for its FRI-specific operations and incur orders-of-magnitude higher
gas. The same constraint forces Ethereum L1 deployments toward BN254
over BLS12-381 in the absence of EIP-2537.

\subsection{Cross-axis dependencies}
\label{sec:dimensions-deps}

The six axes carry the following hard dependencies:

\begin{itemize}
  \item \emph{SNARK $\to$ trusted-setup}. Groth16 forces per-circuit;
    PLONK forces universal-updatable; STARK / Plonky2 / Plonky3 force
    transparent. The trusted-setup axis is reducible in theory, but
    operationally distinct because the ceremony's
    multi-contributor-MPC posture is independent of the SNARK choice.
  \item \emph{SNARK $\to$ post-quantum stance}. Pairing-based SNARKs
    are not PQ; hash-based SNARKs are PQ-conjectured. PQ posture is
    therefore reducible to (SNARK, curve), but again the
    operationally-relevant question --- ``which Grover security level
    does this configuration target?'' --- is one further refinement.
  \item \emph{Anchor chain $\to$ verification host}. The available
    host functions are a property of the chain. Stellar gives
    BLS12-381 pairings; Ethereum gives BN254; Mina gives Pickles;
    Aztec gives UltraPlonk-as-execution-model.
  \item \emph{Verification host $\to$ curve / hash}. The available
    host functions transitively constrain the curve choice when
    in-bytecode verification is uneconomical.
\end{itemize}

The remaining cells of the (axis $\times$ axis) dependency matrix are
soft. The taxonomy's value is that it makes the dependency direction
explicit: a designer who fixes the chain for non-cryptographic reasons
(team familiarity, regulatory posture, fee economics) is implicitly
fixing four of the six axes via the dependency chain
chain~$\to$~host~$\to$~curve~$\to$~SNARK~$\to$~setup, and the only
remaining freedom is the in-circuit hash choice.

Figure~\ref{fig:axes} renders the six axes with example configurations
from \S\ref{sec:configurations} placed at their corresponding points;
the dependency arrows above are visualised as directed edges between
axes.

\input{figures/design-space-axes}
