\section{Per-Dimension Analysis}
\label{sec:analysis}

This section populates five comparison tables across the seven
configurations enumerated in \S\ref{sec:configurations}. The
configurations are referred to throughout by their table-row label
(C1 through C7) before they are formally introduced in
\S\ref{sec:configurations}; readers wanting the full descriptions
should jump ahead. Each table draws claims at one of two confidence
levels:

\begin{itemize}
  \item The row labeled C1 (Stellar~+~BLS12-381~+~PLONK) is
    generated from a first-party benchmark harness whose methodology
    is specified in Appendix~\ref{app:bench} and whose source lives
    in this paper's source tree under \texttt{benchmarks/c1/}; the
    C1 deployment under measurement comprises five Soroban contracts
    whose verifying keys all derive from a single SRS reused from
    the Ethereum Foundation KZG
    ceremony~\cite{eth-kzg-ceremony}, and the harness reports
    per-contract numbers. The aggregate C1 row in each comparison
    table summarizes the five-contract distribution; per-contract
    sub-rows are available in the cost table where the variation
    across contracts is load-relevant.
  \item The row labeled C7 (Stellar~+~hash-based, feasibility branch)
    is also first-party measured, on the same testnet, but at a
    feasibility-only scope: deploy and admin operations measured
    end-to-end; the proof-bearing operations are pending PCS-tied
    prover work. The feasibility harness exists at
    \texttt{benchmarks/c7/}; \S\ref{sec:cfg-c7} discusses what the
    deploy-cost ratio of 590$\times$ tells us about the
    host-function gap and what the missing PCS layer prevents us
    from learning.
\end{itemize}

Rows C2--C6 cite published numbers attributed inline. All USD
figures are anchored to 2026-05 fee-market and spot-rate conditions;
reviewers wanting contemporary numbers should re-run the harnesses
and re-cite (\S\ref{app:bench}, \S\ref{sec:cfg-c7}).

\subsection{Verification cost}
\label{sec:analysis-cost}

Table~\ref{tab:cost} summarizes verification cost. The C1 sub-rows
are populated from the Stellar testnet release \texttt{v0.0.5}
benchmark harness; the C7 deploy and admin rows are populated from
the feasibility-branch harness on the same testnet. The structural
claims the table supports:

\begin{itemize}
  \item \textbf{Native pairing precompiles dominate the cheap end.}
    Configurations whose verifier reduces to a small number of
    pairings called via a host function (C1, C2) are one to two
    orders of magnitude cheaper than configurations whose verifier
    runs the same primitives in pure bytecode. The Stellar
    BLS12-381 pairing host function~\cite{stellar-cap-0059} and the
    Ethereum BN254 pairing precompile (EIP-197) are the components
    that dominate this regime. C1 \texttt{verify\_membership} lands
    at \textasciitilde 79K stroops ($\sim$\$0.003 at the 2026-05
    XLM/USD anchor); C2's BN254-Groth16 verify on Ethereum L1 is
    one-to-two orders of magnitude more expensive in USD even after
    the precompile, dominated by L1 fee-market pressure rather than
    by the verifier shape.
  \item \textbf{Universal updatable schemes carry verifier overhead.}
    PLONK-family verifiers require multiple $\mathbb{G}_1$ and
    $\mathbb{G}_2$ multi-scalar multiplications beyond the pairing
    check; on chains without an MSM precompile, this raises baseline
    verification cost by an additional $2$--$5\times$ over Groth16.
    On Stellar specifically (C1) the overhead is attenuated by
    CAP-0059's $\mathbb{G}_1$ scalar-multiplication and
    $\mathbb{G}_1$ addition host
    functions~\cite{stellar-cap-0059} --- the MSM is decomposed into
    native scalar-mul calls --- but is not eliminated; the C1 row
    sits in the cheap regime, just at a constant-factor disadvantage
    relative to a hypothetical Groth16-on-Stellar configuration.
    Within the five C1 contracts, \texttt{verify\_membership}
    varies by less than 1\% across the 5 verifying-key families
    (78,983--79,168 stroops), confirming that the
    universal-SRS-shared verifier shape dominates over per-relation
    constraint-count differences in the on-chain measurement.
  \item \textbf{Transparent-setup configurations on chains without
    FRI host functions are deployable but expensive.} C7 deploys a
    pure-WASM FRI low-degree-test verifier on Stellar at $1.72$~XLM
    (\textasciitilde\$0.69 USD), a $\sim$590$\times$ multiplier over
    C1's deploy. The deploy-cost ratio is dominated by the verifier
    contract's bytecode footprint --- the Poseidon2 host primitive
    added by Stellar's CAP-0075~\cite{stellar-cap-0075} closes the
    in-circuit-hash sub-gap but does not amortize the
    Merkle-authentication, FRI-folding, or transcript-bookkeeping
    sub-gaps, which collectively dominate the verifier WASM. The
    proof-bearing entrypoints' steady-state cost is pending PCS-tied
    prover work; deploy is the only first-party measurement, but is
    sufficient to refine the §3.6 framing of the
    host-function constraint from binary to gradient.
\end{itemize}

\input{tables/tab-cost-comparison}

\subsection{Proof size}
\label{sec:analysis-size}

Table~\ref{tab:proof-size} ranks configurations by proof size.
Groth16 is uniquely small at constant-size 192~B with BLS12-381
compressed encoding, or 128~B with BN254 (C2)~\cite{groth-2016-onpairing}.
PLONK-family proofs (C1, C3) are $\sim$0.5--1~KB; the C1 row sits
at $\sim$700~B for a vanilla KZG-PLONK proof on BLS12-381 with
compressed encoding (9~$\mathbb{G}_1$ + 7~$\mathbb{F}_r$ elements
in the Gabizon--Williamson--Ciobotaru
construction~\cite{gabizon-2019-plonk}). Recursive schemes (C4,
Mina~+~Pickles) carry the recursion-frame overhead and land in the
10--20~KB range. FRI-based schemes (C5--C7) are the largest at
50--200~KB depending on the security level and FRI rate parameter;
the Plonky2 and Plonky3 lines achieve smaller sizes than classical
STARKs by aggressive use of small fields and recursion within the
proof.

\input{tables/tab-proof-size}

The implication for registry design is direct: configurations whose
proofs travel in transactions on a chain with per-byte fees pay for
proof size linearly. C5--C7's 50--200~KB proofs are economical only
on chains that subsidize ZK-rollup-style submissions; on a general
L1, they are not.

\subsection{Prover wall-clock}
\label{sec:analysis-prover}

Table~\ref{tab:prover-time} reports prover wall-clock for the
canonical advancement relation at a medium ring size (64 members for
systems with a member notion; ``one signal'' for Tornado-shaped
systems). Single-threaded baseline on commodity x86\_64; multi-thread
scaling is reported in Appendix~\ref{app:bench} for C1 and is cited
inline for the others.

The headline ordering is:
\begin{enumerate}
  \item Plonky2/3 (C5, C7) win on prover time at the cost of proof
    size, by virtue of FRI's amenability to GPU- and SIMD-accelerated
    NTT and Merkle-tree workloads on small fields.
  \item Groth16 (C2) is competitive in the medium-circuit regime
    where the relation is well-tuned but degrades at large ring
    sizes; the per-proof cost is dominated by the multi-scalar
    multiplication on $\mathbb{G}_1$.
  \item PLONK-family schemes with KZG commitments (C1, C3) introduce
    additional polynomial-commitment overhead and are typically
    $1.5$--$3\times$ slower than Groth16 at equivalent constraint
    counts. C1's reuse of the EF KZG SRS does not change the
    prover-time profile relative to a same-size project-specific
    KZG ceremony --- the SRS-reuse property is a trust posture, not
    a performance one --- but it does eliminate the per-relation
    Phase-2 ceremony cost that a Groth16 deployment of the same
    five-policy structure would carry.
  \item STARK over Goldilocks (C6) is competitive with Plonky2 in raw
    prover throughput; the difference is a constant factor that
    depends on the specific commitment scheme and the rate parameter.
\end{enumerate}

\input{tables/tab-prover-time}

\subsection{Trust assumptions}
\label{sec:analysis-trust}

Table~\ref{tab:trust} summarizes trust posture along three axes:
trusted-setup ceremony, validator set composition, and operationally
realized censorship resistance.

\input{tables/tab-trust-assumptions}

The trust-assumption ranking is partial-order, not total: Ethereum L1
(C2) wins on validator decentralization but loses to Mina (C4) on
trusted setup; Mina wins on setup but loses to Ethereum on validator
count. The deployment recommendations in
\S\ref{sec:recommendations} navigate this partial order by deployment
profile.

\subsection{Post-quantum posture}
\label{sec:analysis-pq}

Table~\ref{tab:pq} classifies each configuration by the §3.4
post-quantum class. The headline is uncomplicated: every
pairing-based configuration (C1--C5, including the seemingly modern
Plonky2~+~KZG~over~BN254 in C5) is broken under Shor at zero
post-quantum security level; only the FRI-based configurations
(C6, hypothetical C7) carry positive Grover-resistant security. The
C5 case warrants precision: the post-quantum soundness of a deployed
configuration is the minimum of its constituent commitment schemes'
post-quantum soundness, and the outer KZG wrap dominates the
minimum. The inner FRI prover is not irrelevant to C5 --- it remains
post-quantum-secure as a sub-component --- but it is not the
bottleneck; an adversary capable of forging KZG commitments produces
accepted L1 verifications regardless of the inner FRI's properties.
Modernity in the literature is uncorrelated with post-quantum
readiness because the post-quantum decision is orthogonal to
construction novelty.

\input{tables/tab-pq-posture}

The careful caveat about hash-based configurations is that the
Grover-resistant security level depends on the underlying hash, not
on the FRI construction itself. Poseidon and Poseidon2 in their
standard parameter sets target $\sim$128 classical bits, which under
generic Grover speedup gives $\sim$64 post-quantum bits before
parameter doubling. STARK-friendly hashes such as Rescue-Prime are
typically parameterized for $\sim$100 PQ-bits at the cost of
constraint count. The PQ posture column is therefore a property of
the (SNARK $\times$ hash) joint choice, not of the SNARK alone.

\subsection{Synthesis}
\label{sec:analysis-synthesis}

Across all five tables, the configurations group into three regimes:
\emph{cheap pairing-based with native host functions} (C1, C2),
\emph{moderate-cost universal-updatable on chains with sequencers}
(C3, C5), and \emph{post-quantum-ready transparent} (C6 and the
empirically-quantified C7). The cheap-and-PQ-ready cell is empty
along the operationally-relevant censorship-resistance and
decentralization axes: C6 anchored on StarkNet does combine
FRI-friendly host functions with hash-based PQ security at
competitive cost on the L2 itself, but StarkNet's centralized prover
and sequencer place the configuration outside the §7.3
censorship-resistance profile and outside the validator-set tier of
C2. C7 inhabits the same Stellar SCP validator tier as C1 and is
post-quantum-ready, but pays a measured $\sim$590$\times$ deploy
multiplier and is gated on a PCS layer for proof-bearing entrypoints.
The cell that is actually empty is therefore \emph{cheap, PQ-ready,
and decentralized to a tier comparable with C1 or C2}; the
\S\ref{sec:cfg-c7} measurement \emph{quantifies} how far C7 sits
from filling that cell rather than only \emph{describing} the
distance. The open problems of \S\ref{sec:open} discuss the
host-function and tooling moves that would close the gap.
