\section{Migration Paths}
\label{sec:migration}

We now ask: starting from each configuration in
\S\ref{sec:configurations}, what transformations would be required to
reach a post-quantum-ready endpoint, and what blocks each
transformation? We categorize every transformation into one of four
blocker classes:

\begin{enumerate}
  \item[(a)] \textbf{Ready today.} The destination configuration is
    deployable; the transformation is engineering work against
    existing libraries and host functions.
  \item[(b)] \textbf{Blocked on host functions.} The destination is
    cryptographically defined and supported by mature libraries, but
    on the chosen anchor chain the verifier would run in pure
    bytecode at prohibitive gas cost. Unblocked by a chain-protocol
    upgrade adding the relevant precompile or host function.
  \item[(c)] \textbf{Blocked on tooling maturity.} The destination is
    cryptographically defined but lacks a production-grade
    implementation (no audited library, no compiler from the
    relation language to the proving system, no battle-tested setup
    procedure). Unblocked by engineering work outside the deploying
    team's scope.
  \item[(d)] \textbf{Blocked on cryptographic open problems.} The
    destination configuration would require a construction that does
    not yet exist in the literature, or one whose security is open.
    Unblocked only by research progress.
\end{enumerate}

Figure~\ref{fig:migration} renders the resulting migration DAG;
\input{figures/migration-graph}
each subsection discusses transformations from one starting point.

\subsection{From C1 (Stellar + BLS12-381 + PLONK)}
\label{sec:mig-c1}

Three migration paths to a PQ-ready endpoint:

\begin{description}
  \item[\textsc{C1 $\to$ C7} (commitment-scheme swap, hash-based on
    Stellar):] retain the Stellar anchor, swap the KZG
    polynomial-commitment scheme for FRI. Class \textbf{(b/c)}: the
    feasibility-branch deployment in \S\ref{sec:cfg-c7} demonstrates
    that the verifier side of this migration is mechanically
    deployable today --- the Poseidon2 host primitive added by
    CAP-0075~\cite{stellar-cap-0075} carries the in-circuit hash;
    field arithmetic, NTT, Merkle-path traversal, and the
    low-degree-test loop run in pure WASM. The empirical deploy-cost
    multiplier is $\sim$590$\times$ over C1
    (\S\ref{sec:analysis-cost}), and the prover side is gated on a
    PCS layer tying FRI commitments to an AIR --- a tooling gap
    rather than a host-function gap. So the migration is more
    accurately characterised as ``deployable but economically
    biased and tooling-incomplete'' than ``blocked''. A successor
    Stellar CAP adding small-field FRI primitives would close the
    deploy-cost gap; we discuss its technical shape in
    \S\ref{sec:open-host}. The complementary path of swapping FRI
    over Goldilocks for FRI over BN254~$\mathbb{F}_r$ (the
    feasibility-branch pivot) trades small-field prover-time gains
    for in-circuit-hash host-function support, and is the empirically
    cheaper migration today.
  \item[\textsc{C1 $\to$ C6} (anchor change to StarkNet or similar):]
    abandon the Stellar anchor and re-deploy on a chain whose
    verification host is FRI-aware. Class \textbf{(a)}: the
    transformation is implementable today against existing tooling.
    Trade-offs: validator-set composition changes (StarkNet's prover
    is currently centralized; Stellar's $\sim$30-validator SCP is
    qualitatively different), fee market changes, and the team must
    re-audit against a different runtime. The trusted-setup
    posture also changes shape --- C6 has transparent setup
    (no SRS at all), so the EF-KZG provenance chain that C1 carries
    becomes vacuous on the destination side.
  \item[\textsc{C1 $\to$ C1+lattice} (lattice-based polynomial
    commitments):] retain Stellar and the PLONK polynomial IOP,
    instantiate the polynomial-commitment scheme over a PQ-secure
    lattice-based construction in place of KZG. Class \textbf{(d)}:
    no production-grade construction exists.
\end{description}

Figure~\ref{fig:trajectory} renders this trajectory: the recently
completed universal-SRS migration on the left, the host-blocked
in-place PQ migration on the right, and the ready anchor-change
alternative branching downward.

\input{figures/c1-trajectory}

\subsection{From C2 (Ethereum L1 + BN254 + Groth16)}
\label{sec:mig-c2}

\begin{description}
  \item[\textsc{C2 $\to$ STARK on L1} (in-place SNARK swap):] swap
    Groth16 for STARK on Ethereum L1. Class \textbf{(b)}:
    Ethereum L1 has BN254 precompiles (EIP-196/197) and is acquiring
    BLS12-381 precompiles via EIP-2537~\cite{eip-2537}, but no FRI
    host function is on the road-map; pure-bytecode verification is
    prohibitive at L1 gas prices.
  \item[\textsc{C2 $\to$ C6} (anchor change to StarkNet):] re-deploy
    on a FRI-aware L2. Class \textbf{(a)}. Trade-offs: introduces the
    L2 sequencer trust layer; the L1-anchor-only fallback present in
    rollup architectures partially mitigates this.
  \item[\textsc{C2 $\to$ Stellar} (anchor change with curve
    preservation):] re-deploy a Tornado-style construction on
    Stellar without curve change. Class \textbf{(a)} as of Stellar
    Protocol 25, which added native BN254 host
    functions~\cite{stellar-cap-0074} (point addition, scalar
    multiplication, pairing check). A C2 deployer can keep the
    BN254 curve, the BN254-instantiated Groth16 verifying key, the
    Poseidon arithmetization (CAP-0075~\cite{stellar-cap-0075}),
    and the per-circuit MPC ceremony output, and only swap the
    anchor chain and the contract host. Does not improve PQ
    posture; included as a non-PQ migration that changes only the
    trust posture and the fee market. The destination is
    \emph{not} C1: C1's defining axes are PLONK / KZG / EF-SRS, so
    Groth16-on-Stellar-with-BN254 is a distinct point in the
    taxonomy not separately catalogued here.
\end{description}

\subsection{From C3 (Aztec + UltraPlonk)}
\label{sec:mig-c3}

\begin{description}
  \item[\textsc{C3 $\to$ STARK-Aztec} (in-place SNARK family swap):]
    re-implement the Aztec rollup machinery on a hash-based proof
    system, retaining the verifier-as-rollup posture. Class
    \textbf{(c)}: UltraPlonk-on-BN254 is deeply embedded in the
    Aztec architecture (the Noir compiler, the proving server, the
    sequencer's batched-proof aggregator); a STARK-based replacement
    is engineering scale outside the registry deployer's scope.
  \item[\textsc{C3 $\to$ C6} (anchor change):] migrate the registry's
    relations to a STARK-based L2 (StarkNet). Class \textbf{(a)} for
    the relation re-implementation, but the application loses
    Aztec's privacy-as-execution-model semantics. The PQ posture
    improves; the privacy posture changes shape.
\end{description}

\subsection{From C4 (Mina + Pickles + Pasta)}
\label{sec:mig-c4}

\begin{description}
  \item[\textsc{C4 $\to$ FRI-Pickles} (in-place commitment-scheme
    swap):] replace Pasta-cycle commitments with a hash-based
    commitment scheme. Class \textbf{(c)}: Mina's road-map
    discusses this (Kimchi has a PQ trajectory) but no
    production-grade implementation exists. The recursion structure
    of Pickles is an active research area for hash-based
    re-instantiation.
  \item[\textsc{C4 $\to$ C6} (anchor change):] re-deploy on
    StarkNet. Class \textbf{(a)} for the registry, but the
    application loses the protocol-level recursion that makes Mina
    distinctive.
\end{description}

\subsection{From C5 (L2 + Plonky2/3 + KZG over BN254)}
\label{sec:mig-c5}

C5 is the most interesting starting point because the inner prover is
already FRI-based; only the outer KZG wrap is post-quantum-broken.

\begin{description}
  \item[\textsc{C5 $\to$ STARK-wrapped C5} (outer-wrap swap):]
    replace the KZG wrap with a STARK wrap and submit the wrapped
    proof to the L1 verifier. Class \textbf{(b)}: Ethereum L1 lacks
    a FRI host function; the wrapped proof verifies in pure bytecode
    at uneconomical gas. On an L1 with FRI host functions, this is
    Class (a).
  \item[\textsc{C5 $\to$ C6} (drop the L1 anchor):] settle directly
    on a FRI-aware L2 such as StarkNet, eliminating the need for the
    KZG wrap entirely. Class \textbf{(a)}. The L1-anchor-only
    fallback property is lost; configurations that depend on it must
    decline this migration.
\end{description}

\subsection{From C6 (STARK over Goldilocks)}
\label{sec:mig-c6}

C6 is already PQ-ready. Migrations from C6 are about
\emph{portability} rather than PQ posture: which chains can host the
configuration?

\begin{description}
  \item[\textsc{C6 portability to Stellar}:] equivalent to the
    \textsc{C1 $\to$ C7} path. Class \textbf{(b)}.
  \item[\textsc{C6 portability to Ethereum L1}:] equivalent to the
    \textsc{C2 $\to$ STARK-on-L1} path. Class \textbf{(b)}.
  \item[\textsc{C6 portability to FRI-aware L2}:] Class \textbf{(a)};
    StarkNet, Polygon zkEVM with FRI inner layer, and similar chains
    accept the configuration directly.
\end{description}

\subsection{From C7 (Stellar + hash-based, feasibility branch)}
\label{sec:mig-c7}

C7 is the asymmetric case: post-quantum-ready, deployable today at
$\sim$590$\times$ the deploy footprint of C1 with proof-bearing
entrypoints not yet end-to-end measurable, and inhabiting the
host-function-cheap regime only after either a Stellar host-function
upgrade or a tooling completion.

\begin{description}
  \item[\textsc{Stellar protocol upgrade adding small-field FRI
    primitives}:] Class \textbf{(b)}. Protocol 25 has already moved
    part of the way: CAP-0075~\cite{stellar-cap-0075} added Poseidon
    and Poseidon2 permutation primitives over the existing scalar
    fields (BLS12-381~$\mathbb{F}_r$, BN254~$\mathbb{F}_r$). What
    closes the empirical deploy-cost gap is the orthogonal subset
    that CAP-0075 explicitly declined to introduce: Goldilocks-field
    arithmetic, NTT, FRI-folding, and Merkle-path-traversal
    primitives over a small field. The CAP's rationale documents
    this scope decision; it is deliberate rather than oversight. A
    successor CAP would need to introduce a new field arithmetic to
    the host-function ABI, which is a larger commitment than
    CAP-0075 was willing to make. We estimate the engineering scale
    of the unblock at one to two chain-protocol-upgrade cycles plus
    validator activation; we do not estimate the political
    feasibility, which is the load-bearing variable in practice.
  \item[\textsc{Tooling completion --- PCS layer tying FRI to an
    AIR}:] Class \textbf{(c)}. The feasibility-branch verifier today
    accepts a FRI low-degree-test proof but no batched-PCS layer
    binds those FRI commitments to an evaluation of a constrained
    polynomial in an AIR. Closing this gap requires either a
    Plonky3-style PCS implementation against the Stellar
    Poseidon2-W16 transcript, or a Cairo-style alternative AIR
    encoding; neither exists at production-grade maturity in the
    feasibility branch. Until this layer lands, the C7 row's
    proof-bearing entrypoints remain not-first-party-measurable and
    the steady-state verification cost of C7 is bounded only by the
    \S\ref{sec:analysis-cost} estimate.
\end{description}

\subsection{Migration matrix}
\label{sec:migration-matrix}

\begin{table}[t]
  \centering
  \caption{Migration blocker class for each (start, end) pair where
    the end is one of the post-quantum-ready configurations
    surveyed. Columns are restricted to PQ-ward destinations because
    the migration question this section asks is the PQ-readiness
    question; non-PQ migrations between configurations are tabulated
    in the per-subsection prose above. ``--'' indicates the
    transformation is undefined or trivially the identity.}
  \label{tab:migration}
  \begin{tabular}{lccc}
    \toprule
    Start & $\to$ C6 & $\to$ C7 & lattice path \\
    \midrule
    C1 & (a) & (b/c)$^\flat$ & (d) \\
    C2 & (a) & ---  & (d) \\
    C3 & (a)$^\ast$ & --- & (d) \\
    C4 & (a)$^\ast$ & (c)$^\dagger$ & (d) \\
    C5 & (a) & (b/c)$^\flat$ & (d) \\
    C6 & ---  & (b/c)$^\flat$ & (d) \\
    C7 & (b/c)$^\flat$ & ---  & (d) \\
    \bottomrule
  \end{tabular}
  \\[0.5em]
  \footnotesize
  $^\ast$ The migration is technically Class (a) but loses
    application-relevant semantics (verifier-as-rollup for C3,
    protocol-level recursion for C4). \\
  $^\dagger$ FRI-Pickles is the C4 in-place migration; included
    for completeness in the C7-shaped destination column. \\
  $^\flat$ Refined from earlier-draft Class (b) ``host-function
    blocked'' to (b/c) ``deployable today, deploy at $\sim$590$\times$
    C1, proof-bearing entrypoints additionally tooling-blocked on a
    PCS layer'', based on the feasibility-branch measurement of
    \S\ref{sec:cfg-c7}.
\end{table}

The matrix carries one observation that drives \S\ref{sec:open}: no
column is uniformly Class (a). Either the migration is operational
(anchor change), losing some property; or it is blocked on host
functions; or it is blocked on tooling; or it is open. The
deployment recommendations of \S\ref{sec:recommendations} navigate
this landscape by starting position and priority weighting rather
than by attempting to identify a globally dominant migration.
