\section{Recommendations by Deployment Profile}
\label{sec:recommendations}

The taxonomy of \S\ref{sec:dimensions}, the cost and trust analysis
of \S\ref{sec:analysis}, and the migration analysis of
\S\ref{sec:migration} together imply that \emph{no configuration
dominates}. Different deployment profiles --- different priorities
weighted at different operational scales --- land on different
configurations. We present four profiles. Each is intentionally
narrow, so that a real deployment that lies between two profiles can
inspect both and decide. Table~\ref{tab:recommendations} summarizes.

\subsection{Cost-optimized profile}
\label{sec:rec-cost}

\textbf{Priority.} Minimize USD per verification at the deployed scale.
PQ posture, validator decentralization, and jurisdictional
constraints are accepted as given.

\textbf{Recommendation.} \textbf{C1} (Stellar~+~BLS12-381~+~PLONK).
The combination of native pairing and $\mathbb{G}_1$
scalar-multiplication host
functions~\cite{stellar-cap-0059} and Stellar's flat-fee resource
metering puts C1 at the cheap end of Table~\ref{tab:cost}. C2
(Ethereum L1) is structurally similar at the SNARK layer (with the
SNARK-family difference noted below) but loses on the L1 fee
market; the order of magnitude separating the two is consistent
across the deployment-volume range we examined.

\textbf{Trade-offs.} PLONK's universal SRS posture (instantiated by
reuse of the Ethereum Foundation KZG
ceremony~\cite{eth-kzg-ceremony}) eliminates the per-relation
trusted-setup overhead a Groth16 deployment of the same five-policy
structure would carry, at the cost of a constant-factor
verification overhead from the multi-scalar-multiplication shape of
the PLONK verifier (\S\ref{sec:analysis-cost}). The trusted-setup
trust assumption is one-honest-of-${\sim}141{,}000$ contributors
--- structurally stronger than any small-N ceremony a single
deploying team could realistically run. PQ posture remains zero.
Stellar's $\sim$30-validator SCP set is at the lower end of
decentralization within the surveyed configurations.

\textbf{Non-recommendation.} Cost-optimized deployments should not
adopt C5 or C6: the L2-anchored configurations carry sequencer trust
overhead the cost-optimized profile does not benefit from, and FRI
proof sizes invert the per-byte fee economics on chains without FRI
host functions.

\subsection{Post-quantum-prioritized profile}
\label{sec:rec-pq}

\textbf{Priority.} Minimize residual cryptographic risk under a
fault-tolerant adversary running Shor on the SNARK's underlying
hardness assumption. Cost, validator count, and operational maturity
are accepted as a function of the chosen anchor.

\textbf{Recommendation.} \textbf{C6} (STARK over Goldilocks anchored
on a FRI-aware chain). C6 is the unique configuration in the
surveyed set that combines transparent setup with hash-based
post-quantum security and a deployable verification host. Anchor
selection within C6 is a sub-decision: StarkNet has a centralized
prover and is changing rapidly; a self-hosted FRI-aware rollup is an
option for deployments at scale.

\textbf{Trade-offs.} Verification cost is one to two orders of
magnitude higher than C1/C2 in absolute USD; proof sizes are 50--200
KB; the operational stack (Cairo, the StarkNet runtime, and the
proof aggregator) is distinct from the Ethereum-derived stacks the
deployer's team is more likely to be familiar with.

\textbf{Non-recommendation.} The PQ-prioritized profile should
\emph{not} adopt C5 (Plonky2/3~+~KZG over BN254). The configuration's
inner FRI prover is post-quantum-secure but its outer KZG wrap
nullifies that property at the verification layer, and the
configuration is sometimes marketed as PQ-ready in ways the actual
verification chain does not support
(\S\ref{sec:cfg-c5}).

\subsection{Censorship-resistance-prioritized profile}
\label{sec:rec-censorship}

\textbf{Priority.} Maximize the difficulty of preventing an
authorized state-transition transaction from reaching inclusion.
Three sub-properties are weighted: validator-set size and stake
distribution, sequencer / proposer dependence, and trusted-setup
single-point-of-failure.

\textbf{Recommendation.} \textbf{C2} (Ethereum L1~+~BN254~+~Groth16)
\textbf{with a multi-contributor MPC ceremony, or the
universal-SRS-on-Stellar shape of C1 if the trapdoor axis is the
binding concern}. Ethereum L1's $\sim$10$^6$-staker validator set
dominates the chain-validator column of Table~\ref{tab:trust} by
orders of magnitude over every other surveyed anchor and is the
unique reason to pick C2 for this profile. The trapdoor-knowledge
axis, formerly the dominant single-point-of-failure for C2's
per-circuit MPC, is no longer privileged in the choice between C1
and C2: C1's reuse of the EF KZG
ceremony~\cite{eth-kzg-ceremony} places its trapdoor-honesty
assumption at one-of-${\sim}141{,}000$ contributors, strictly
stronger than the $n \approx 10^3$ contributor scale a Tornado-style
C2 ceremony has historically achieved. A deployer for whom the
trapdoor axis is the binding concern --- as opposed to the
chain-validator-set decentralization axis --- should select C1; a
deployer for whom the chain-validator axis is binding should select
C2 with a multi-contributor MPC.

\textbf{Trade-offs.} Selecting C2 incurs higher per-verification
cost than C1 and a per-relation ceremony cost that recurs on
relation upgrades; PQ posture is zero. Selecting C1 in this profile
trades chain-validator-set decentralization for the universal-SRS
posture and Stellar's lower fee schedule.

\textbf{Non-recommendation.} L2-anchored configurations (C3, C5)
introduce sequencer dependence that the censorship-resistance
profile cannot accept regardless of the L1-anchor-only fallback's
operational properties; the fallback is a recovery path, not a
real-time censorship resistance property. C6 anchored on StarkNet
loses on the same axis.

\subsection{Jurisdictional-constraints profile}
\label{sec:rec-jurisdiction}

\textbf{Priority.} Compliance with operational constraints imposed
by regulation, sanctions enforcement, data-residency requirements,
or contractual obligations to specific jurisdictions. The
constraints are not cryptographic; the deployment question is
whether any of the surveyed configurations are operationally
acceptable.

\textbf{Recommendation.} The honest answer is that the surveyed
configurations \textbf{do not directly serve this profile}. A
permissionless public chain hosts the registry whether or not the
deploying entity wishes it, and the metadata-hiding properties the
configuration provides operate against an adversary that includes
regulators by definition. A jurisdiction-constrained deployment
should consider:
\begin{itemize}
  \item A \textbf{private rollup} with the configuration's relation
    structure preserved but the verifier hosted on permissioned
    infrastructure. This sacrifices the metadata-hiding-against-the-
    operator property in exchange for jurisdictional control.
  \item An \textbf{off-chain registry} backed by a cryptographic
    audit trail. The advancement abstraction degrades, but
    verifiability against a public audit set is preserved.
  \item A \textbf{redeployment on a permissioned anchor} (Hyperledger
    Besu, Quorum, etc.) with the same SNARK family but
    permissioned validation.
\end{itemize}
None of these are configurations in the surveyed taxonomy. We flag
the gap rather than paper over it.

\textbf{Non-recommendation.} A jurisdiction-constrained deployment
should not adopt C1, C2, C3, C4, C5, or C6 without first answering
the operator question: against whom are the metadata-hiding
properties offered? If the answer includes a regulator, the
metadata-hiding property and the regulatory-compliance property are
in direct tension and must be resolved before any taxonomy choice.

\subsection{Summary}
\label{sec:rec-summary}

\begin{table}[t]
  \centering
  \caption{Recommendations by deployment profile.}
  \label{tab:recommendations}
  \begin{tabularx}{\columnwidth}{@{}lXl@{}}
    \toprule
    Profile & Recommendation & Don't \\
    \midrule
    Cost              & C1 & C5, C6 \\
    Post-quantum      & C6 & C5 \\
    Censorship res.   & C2 (multi-ctb.\ MPC), or C1 if trapdoor is binding & C3, C5, StarkNet-C6 \\
    Jurisdictional    & None of C1--C6 & C1--C6 \\
    \bottomrule
  \end{tabularx}
\end{table}

The table is intentionally short and the columns intentionally narrow.
A deployment that does not match any single profile should treat the
profiles as anchor points and weight between them. The migration
analysis of \S\ref{sec:migration} provides the cost of moving from a
chosen starting configuration toward an alternative profile; the
combined reading is that profile-conditional recommendations are
robust under small priority shifts, but flip to a different
recommendation when the priority weighting changes more than one
profile's worth.
