\section{Open Problems}
\label{sec:open}

The taxonomy of \S\ref{sec:dimensions}, the analysis of
\S\ref{sec:analysis}, and the migration matrix of
\S\ref{sec:migration} together make eight open problems legible. Some
are research questions that have been studied but not closed; others
are engineering gaps that no single deployer can close on their own.
We list them in decreasing order of how directly they would
unblock the recommendations of \S\ref{sec:recommendations}.

\paragraph{(1) Cheap and post-quantum.} Section~\ref{sec:analysis}'s
synthesis named three configuration regimes and observed that the
cheap-and-PQ-ready cell is empty. No surveyed configuration combines
native-host-function-cheap verification with hash-based
post-quantum security. The closest candidates are C7 (blocked on
host functions) and C6 (PQ-ready but at proof sizes that invert
per-byte fee economics on most anchor chains). Closing this gap
requires either a chain protocol upgrade adding FRI-friendly host
functions to a chain that currently has only pairing host functions
(\S\ref{sec:open-host} below), or a SNARK construction that targets
both pairing-friendly verifier costs and post-quantum security
simultaneously --- which is one phrasing of open problem (4).

\paragraph{(2) Hash-based recursion at production proof
sizes.} Plonky2~\cite{plonky2-2022} and
Plonky3~\cite{plonky3-spec} achieve competitive prover wall-clock by
aggressive use of small fields and FRI commitments, and they support
recursion. However, recursive FRI proofs do not currently land at
proof sizes competitive with KZG-wrapped equivalents on
size-sensitive anchors. The lower bound on FRI proof size at fixed
security level is a research-level question with active
work; for an applied SoK reader, the operationally-relevant
question is when the existing proof-size gap closes by a factor
sufficient to make pure-FRI L1-anchored deployment economical.

\paragraph{(3) Non-pairing host functions on chains whose existing
host-function set is curve-centric.}
\label{sec:open-host}
Stellar's host-function trajectory is the cleanest illustration of the
shape of this gap. Protocol 22 added {BLS12-381} host
functions~\cite{stellar-cap-0059}; Protocol 25 added {BN254}
host functions~\cite{stellar-cap-0074} and Poseidon / Poseidon2
permutation primitives over {BLS12-381}~$\mathbb{F}_r$ and
{BN254}~$\mathbb{F}_r$~\cite{stellar-cap-0075}. The
trajectory tracks pairing-based and Poseidon-arithmetization
deployments well; what it does not track is the FRI stack.
{CAP-0075}'s rationale explicitly scopes \emph{out} {NTT}
primitives, Goldilocks-field arithmetic, and FRI-related operations,
on the grounds that exposing permutation primitives over the
existing scalar fields is more flexible than introducing a new field
arithmetic. The decision is defensible in isolation but it leaves
the FRI configurations (C6, C7) with no host-function support on the
chain. The right ABI for a chain that wants to support both
pairing-based and FRI-based SNARKs simultaneously is itself an open
design question, and surveys of which primitives are most reusable
across SNARK families are currently missing from the literature.

\paragraph{(4) Transparent setup with pairing-friendly verification.}
Every pairing-based SNARK in current production deployment requires a
setup ceremony, either per-circuit (C1, C2) or universal-updatable
(C3, C5). A construction that preserves the
verifier-cost properties that make pairing-based schemes attractive
on chains with pairing precompiles, while eliminating the ceremony,
would land at a particularly useful point in the taxonomy. The
existing transparent-setup constructions occupy the
opposite corner: Halo2 with IPA, Spartan, Bulletproofs~\cite{bunz-2018-bulletproofs}
all achieve transparent setup but trade away the
pairing-friendly verifier shape. Closing the gap from either
direction --- adding transparent setup to a Groth16-shaped verifier,
or adding pairing-friendly verification to a transparent-setup
construction --- is open.

\paragraph{(5) PQ migration without a proof-system change.} The §6
migration matrix shows that every PQ-ward migration entails either an
anchor-chain change or a SNARK-family change. A migration that
preserves the proof system, the SRS, and the chain anchor while
upgrading the post-quantum class --- by, for instance, replacing the
underlying curve with a PQ-secure pairing analogue --- does not
currently exist as a construction. Whether a curve-only substitution
that preserves the Groth16-shape or PLONK-shape verifier is
achievable is an open cryptographic question; if it is achievable,
it would collapse the cost of
\S\ref{sec:recommendations}'s PQ-prioritized recommendation by
allowing C1 and C2 deployers to migrate in place. C1's PLONK
choice softens this problem one half-step: the polynomial-commitment
scheme is a more localized point of substitution than the entire
verifier, and a hypothetical lattice-based polynomial-commitment
construction would let C1 migrate without changing the relation
circuits (\S\ref{sec:mig-c1}'s C1 $\to$ C1+lattice path).

\paragraph{(6) Lattice-based SNARKs in production.} Lattice-based
SNARK constructions are an active area of cryptographic research, but
no production deployment we surveyed uses them. The reasons are
operational: prover memory is high; verifier costs are not yet
competitive with KZG-based schemes on chains with pairing precompiles;
no compiler from a circuit DSL to a deployed verifier exists at the
maturity level of the Groth16, PLONK, or STARK toolchains. Tracking
lattice-SNARK readiness for inclusion in a future revision of the
taxonomy is a moving target; the question is when, not whether, they
become a deployable point.

\paragraph{(7) Formal verification of the full SNARK pipeline.}
Existing formal-verification work in the SoK literature largely
covers the underlying relation: a correctness theorem that an honest
prover can produce an accepting proof, a soundness theorem that no
adversary can. The pipeline from the relation to the deployed
verifier --- the circuit compiler, the proving-key serialization,
the contract that calls host functions, the host-function semantics
--- is verified piecemeal at best. End-to-end verification of a
metadata-hiding registry deployment, from a high-level relation
specification through to the on-chain verifier bytecode, is an
engineering project at the scale of the seL4 verification effort and
has not been attempted. The §7.3 censorship-resistance profile and
the §7.4 jurisdictional profile would both materially benefit from
such a verification existing.

\paragraph{(8) Operator-aware metadata-hiding against
jurisdiction-bound adversaries.} \S\ref{sec:rec-jurisdiction}
identified an adversary class --- regulators, sanctions enforcement,
contractual oversight bodies --- that the surveyed configurations'
threat models do not address. The cryptographic literature on
\emph{verifiable disclosure} and on \emph{auditable
zero-knowledge}~\cite{don-2019-fiat-shamir} has begun to address this
class, but none of those constructions is sufficiently mature to add
to the taxonomy as a deployable configuration. A future SoK revision
should treat jurisdictional-aware metadata-hiding as its own
configuration class rather than as a non-recommendation. We flag
this here so that future work can build on the present taxonomy
without re-doing it.

\subsection{Synthesis}

The eight open problems above cluster into three groups: chain-host
gaps (1, 3) that block deployment patterns the cryptography already
supports; cryptographic-construction gaps (2, 4, 5, 6) that require
research progress; and verification and threat-model gaps (7, 8) that
require engineering at scale outside any single deployer's
capacity. The taxonomy's value is partly in making the
\emph{interactions} between these gaps visible: closing (3) without
also closing (2) yields a deployable hypothetical C7 at competitive
cost but inferior proof size; closing (5) without also closing (6)
preserves the deployment shape of C1 / C2 but does not introduce a
fundamentally new point in the design space.
