\section{Conclusion}
\label{sec:conclusion}

We presented a Systematization of Knowledge for metadata-hiding group
registries with SNARK-gated state changes, structured as a six-axis
taxonomy that indexes by deployment constraint rather than by
construction family. Across seven concrete configurations and five
comparison dimensions, the dominant finding is that no configuration
sits in every priority's preferred regime: the cheap-and-not-PQ
regime (C1, C2), the PQ-ready-but-large-proof regime (C6), and the
host-function-blocked hypothetical (C7) form a partial order, not a
total one. The deployment recommendations of
\S\ref{sec:recommendations} are accordingly profile-conditional, and
two of the four profiles point to configurations that would not be
selected under the profile-blind reading of the comparison tables.

For protocol designers, the cross-axis dependency analysis of
\S\ref{sec:dimensions-deps} is the actionable contribution:
fixing the anchor chain for non-cryptographic reasons --- team
familiarity, regulatory posture, fee economics --- implicitly fixes
four of the six axes, leaving only the in-circuit hash truly free.
Designers who treat the chain choice as independent of the
proof-system choice underestimate the constraint they have already
accepted.

For the cryptographic-research community, the migration matrix of
\S\ref{sec:migration-matrix} and the open-problem cluster of
\S\ref{sec:open} together identify the gap: among PQ-ward
destinations, no column of the matrix is uniformly Class~(a), and
the empty cheap-PQ-ready-and-decentralized cell of
\S\ref{sec:analysis-synthesis} is closed only by progress on either
chain-host-function ABIs that admit FRI primitives, or on
SNARK constructions that combine pairing-friendly verifier costs
with hash-based post-quantum security. The path of least research
risk is the chain-host axis; the path of greatest impact is the
SNARK-construction axis.

Future work in two directions is concrete enough to commit to a
follow-up SoK. First, an updated taxonomy that admits a fourth
post-quantum class --- lattice-based --- once a deployable
construction in that class exists. Second, an extension of the
abstraction to operator-aware metadata-hiding against
jurisdiction-bound adversaries (open problem~8); the threat model in
\S\ref{sec:problem} explicitly excludes this adversary class today,
and the taxonomy will need a corresponding extension before that
extension can be made.
