% Cryptographic Soundness of a SNARK-Gated Group-Membership
% Update Contract
%
% A focused whitepaper that traces the authorisation-soundness
% claim of a SNARK-gated group-membership keystone — the general
% "any current member admits a new leaf at a previously-empty
% position" construction — down to base cryptographic
% assumptions, via a compositional reduction.
%
% Build:  make           → main.pdf
%         make clean

\documentclass[11pt,a4paper]{article}

% ─── Packages ────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,shapes.geometric,fit,calc}
\usepackage{xcolor}
\usepackage{cite}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\usepackage{parskip}
\usepackage{enumitem}

% Slightly tighter line spacing for a denser whitepaper feel.
\linespread{1.05}

% ─── Theorem environments ───────────────────────────────────────────
% Each environment gets its own counter so cleveref can label cross-
% references correctly (e.g. \Cref{lem:kzg} prints "Lemma 1", not
% "Theorem 1").
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

% Cleveref name overrides (capital and lowercase forms).
\crefname{theorem}{Theorem}{Theorems}
\Crefname{theorem}{Theorem}{Theorems}
\crefname{lemma}{Lemma}{Lemmas}
\Crefname{lemma}{Lemma}{Lemmas}
\crefname{proposition}{Proposition}{Propositions}
\Crefname{proposition}{Proposition}{Propositions}
\crefname{corollary}{Corollary}{Corollaries}
\Crefname{corollary}{Corollary}{Corollaries}
\crefname{definition}{Definition}{Definitions}
\Crefname{definition}{Definition}{Definitions}
\crefname{assumption}{Assumption}{Assumptions}
\Crefname{assumption}{Assumption}{Assumptions}
\crefname{remark}{Remark}{Remarks}
\Crefname{remark}{Remark}{Remarks}

% ─── Macros ─────────────────────────────────────────────────────────
\newcommand{\Fr}{\mathbb{F}_r}
\newcommand{\Fp}{\mathbb{F}_p}
\newcommand{\GG}{\mathbb{G}}
\newcommand{\GT}{\mathbb{G}_T}
\newcommand{\Gone}{\mathbb{G}_1}
\newcommand{\Gtwo}{\mathbb{G}_2}
\newcommand{\Cg}{C_g}
\newcommand{\Cgp}{{C_g^{\prime}}}
\newcommand{\RMem}{\mathsf{R}_{\mathsf{Mem}}}
\newcommand{\RUpd}{\mathsf{R}_{\mathsf{Upd}}}
\newcommand{\negl}{\mathsf{negl}}
\newcommand{\Hash}{\mathsf{H}}
\newcommand{\Poseidon}{\mathsf{Poseidon2}}
\newcommand{\Adv}{\mathcal{A}}
\newcommand{\Setup}{\mathsf{Setup}}
\newcommand{\Prove}{\mathsf{Prove}}
\newcommand{\Verify}{\mathsf{Verify}}
\newcommand{\Commit}{\mathsf{Commit}}
\newcommand{\Open}{\mathsf{Open}}
\newcommand{\concat}{\mathbin{\|}}
\newcommand{\Empty}{\mathsf{EMPTY}}
\newcommand{\MerkleVerify}{\mathsf{MerkleVerify}}
\newcommand{\MerkleRoot}{\mathsf{MerkleRoot}}
\newcommand{\Idx}{\mathsf{idx}}
\newcommand{\Pth}{\mathsf{path}}

% ─── Title block (brand-neutral, no author) ──────────────────────────
\title{Cryptographic Soundness of a SNARK-Gated Group-Membership Update Contract:\\
       A Compositional Proof Sketch for the Keystone Construction}

\author{}
\date{}

% ─── Document ────────────────────────────────────────────────────────
\begin{document}
\maketitle

\begin{abstract}
We give a compositional proof sketch for the authorisation
soundness of a SNARK-gated group-membership update contract --- a
\emph{keystone construction} that maintains a public commitment
to a membership set and admits state changes only via succinct
non-interactive proofs of a fixed update relation. The relation
analysed here encodes the general admission rule that any
current group member may write any new leaf at a
previously-empty position of the membership commitment, without
quorum, founder set, or admin override; it is the most permissive
admission rule consistent with cryptographic membership soundness,
and richer policies (quorum, founder set, threshold, admin)
tighten the predicate further but require their own
state-transition analyses. The contract sits on top of a fixed
cryptographic stack --- the BLS12-381 curve, the KZG
polynomial-commitment scheme, the Poseidon2 algebraic hash, a
binary Merkle commitment to the membership set, the Fiat--Shamir
transform, and a specific PLONK variant for which
simulation-extractable knowledge soundness has been established
in the literature --- with each layer contributing a single
concrete soundness reduction. The update relation is defined so
that an admission requires \emph{two} Merkle witnesses --- one
for the admitter's own membership, one for the target slot's
emptiness, at distinct leaf positions --- and the Merkle soundness
step is the position-binding statement at a fixed index, not a
path-uniqueness statement. We make every reduction explicit and
trace the contract's authorisation claim down to four base
assumptions: the $d$-strong Bilinear Diffie--Hellman ($d$-SBDH)
problem on BLS12-381, collision resistance of the Poseidon2
permutation under its published parameters, the random-oracle
modelling of Poseidon2 inside the Fiat--Shamir transcript, and
the one-honest-contributor assumption of the reused structured
reference string. The result is a self-contained checklist of
what must hold for the contract to be sound, and a precise
statement of what fails first under a cryptographically-relevant
quantum computer.
\end{abstract}

\section{Introduction}
\label{sec:intro}

A growing class of smart contracts replaces application-layer
trust with a single algebraic check: the contract accepts a
state-changing transaction if and only if the transaction carries
a succinct non-interactive proof that the proposed state change
is well-formed under a published relation. The proof is verified
on chain; the contract never needs to see the prover's witness.

We focus on a concrete instance of this pattern: a group
registry that maintains a public commitment $\Cg$ to a
membership set and transitions $\Cg \mapsto \Cgp$ only when
accompanied by a PLONK~\cite{gabizon-2019-plonk} proof of a fixed
update relation $\RUpd$. We call this construction the
\emph{group-membership keystone}: a single relation that, when
gated by the SNARK, defines who may extend the committed set and
how.

The keystone relation analysed in this paper encodes the
most permissive admission rule that is still consistent with
cryptographic membership soundness: \emph{any current member may
admit any new leaf at a previously-empty position of the
membership commitment}, with no quorum, founder set, or admin
override. This minimum-predicate construction is the easiest to
reason about, and it is the natural base case against which
richer admission rules (quorum, founder set, threshold, admin,
revocation) are variants. Each richer variant adds in-circuit
invariants and therefore requires its own state-transition
analysis (\Cref{cor:family}); the cryptographic-stack reductions
below port unchanged.

\paragraph{Contribution.} We make every link in the soundness
chain explicit. For each cryptographic layer between the
on-chain authorisation check and a base hardness assumption, we
state a single reduction lemma; we then compose them into the
top-level soundness theorem. This gives a self-contained
checklist of what must hold for the contract to be sound, and a
precise statement of what fails first --- and what survives ---
under a cryptographically-relevant quantum computer.

\paragraph{Scope.} The paper covers cryptographic soundness
only. We do not analyse the governance semantics of richer
admission rules, the messaging layer that may sit above the
registry, or the broader economic or operational properties of
any deployment. Each layer of the stack has an established body
of results behind it; we cite the original constructions rather
than reproving them, and present only the composition.

\paragraph{Outline.} \Cref{sec:system} fixes the stack and the
contract. \Cref{sec:threat} states the threat model.
\Cref{sec:defs} gives the formal definitions. \Cref{sec:reductions}
presents the layer-by-layer reductions, \Cref{sec:theorem} composes
them into the top-level soundness statement. \Cref{sec:pq}
addresses post-quantum security. \Cref{sec:notes} catalogues the
implementation discipline the proof depends on.

\section{System overview}
\label{sec:system}

The registry is parameterised by a fixed cryptographic stack;
each layer below is consumed by exactly one layer above (and the
contract sits on top of them all). We summarise each layer here
and refer to the originating literature.

\paragraph{Curve --- BLS12-381.}
A pairing-friendly elliptic curve in the Barreto--Lynn--Scott
family with embedding degree $k=12$ and a 381-bit base
field~\cite{bowe-2017-bls12381}. We work with its two prime-order
subgroups $\Gone, \Gtwo$, the target group $\GT \subset
\Fp^{12}$, the bilinear non-degenerate pairing
$e \colon \Gone \times \Gtwo \to \GT$, and the scalar field
$\Fr$. The 2016 Kim--Barbulescu extended tower number-field
sieve~\cite{kim-barbulescu-2016} fixed the conservative
classical-security target at roughly 120--128 bits.

\paragraph{Polynomial commitment --- KZG.}
The pairing-based polynomial commitment scheme of Kate,
Zaverucha, and Goldberg~\cite{kate-2010-kzg}. A commitment $[f]_1
\in \Gone$ to a polynomial $f \in \Fr[X]$ of degree at most $d$
is a single $\Gone$ element, and an opening at any evaluation
point $z$ is a single $\Gone$ element. Verification is one
pairing check against a structured reference string
$\{[\tau^i]_1, [\tau^i]_2\}_{i=0}^{d}$, where $\tau \in \Fr$ is
the trapdoor.

\paragraph{Algebraic hash --- Poseidon2.}
A sponge-mode hash over $\Fr$ built from a substitution--%
permutation network with $\alpha$-power S-boxes and an MDS linear
layer~\cite{grassi-2023-poseidon2}, refining the original Poseidon
construction~\cite{grassi-2021-poseidon}. We use the canonical
$t=3$ rate-2 / capacity-1 instance with $\alpha = 5$, $R_F = 8$
full rounds, and $R_P = 56$ partial rounds; the round constants
and MDS matrix are the published canonical set.

\paragraph{Membership commitment --- Merkle tree.}
A binary Merkle tree~\cite{merkle-1989-tree} whose internal nodes
are Poseidon2 compressions of their two children. The leaf at
position $i$ encodes a member's identity commitment; the tree's
root is the public group commitment $\Cg$. An authentication
path consists of the sibling hash at every level between the
target leaf and the root.

\paragraph{NIZK transform --- Fiat--Shamir.}
The standard transform of Fiat and
Shamir~\cite{fiat-shamir-1986} that converts a public-coin
interactive proof into a non-interactive one by replacing each
verifier challenge with the hash of the transcript so far. The
hash is Poseidon2; the transcript is opened with a
relation-specific and circuit-binding domain tag, and every
public input is absorbed before any verifier challenge is drawn.
The modern multi-round security analysis is due to Don, Fehr,
Majenz, and Schaffner~\cite{don-2019-fiat-shamir}.

\paragraph{Proof system --- PLONK.}
A universal-updatable preprocessing SNARK for arithmetic
circuits over $\Fr$~\cite{gabizon-2019-plonk}, with polynomial
commitments via KZG and challenges drawn via Fiat--Shamir. Proofs
are constant-size at roughly seven hundred bytes; verification is
one pairing plus a multi-scalar multiplication. The
universal-updatable setup means that the same structured
reference string supports every circuit in the family; the
deployment reuses the SRS produced by the Ethereum Foundation KZG
Summoning Ceremony~\cite{eth-kzg-ceremony}, with provenance
pinned via SHA-256~\cite{nist-fips-180-4} into the
verifying-key supply chain.

\paragraph{On-chain verifier --- Stellar Soroban.}
The PLONK verifier is implemented as a Soroban smart contract on
Stellar, calling host functions for BLS12-381 group operations
and pairings~\cite{stellar-cap-0059} and for Poseidon and
Poseidon2~\cite{stellar-cap-0075}. The verifier holds the
verifying key for the $\RUpd$ circuit; richer admission rules
would compile to distinct $\RUpd$ circuits and to distinct
verifying keys, but the on-chain verification surface
(pairing host functions, transcript replay) is identical across
all such variants.

\paragraph{The keystone contract.}
The on-chain contract accepts a transaction $(\Cgp, \pi)$ and
proceeds as follows. It checks that the public input encoded in
$\pi$ matches its currently-stored root $\Cg$; it calls the
on-chain PLONK verifier with the verifying key for the $\RUpd$
circuit; if verification succeeds, it overwrites $\Cg \mapsto
\Cgp$ in storage, increments an epoch counter, and emits an
admission event. The predicate embedded in the $\RUpd$ circuit
is the keystone predicate: a current member writes a new leaf at
a previously-empty position. We analyse this predicate
throughout; richer policies replace it with a tighter one
(\Cref{cor:family}).

\section{Threat model}
\label{sec:threat}

We adopt a standard SNARK adversary. The adversary $\Adv$ is a
probabilistic polynomial-time algorithm. It is given the full
public state of the system: the verifying key for the keystone
$\RUpd$ circuit (and for any other circuit deployed alongside it
under the same SRS), the current group commitment $\Cg$, the
epoch counter, every event emitted to date, and the full
structured reference string $\{[\tau^i]_1, [\tau^i]_2\}_{i=0}^{d}$
(the SRS is public --- only the trapdoor $\tau$ is secret).
$\Adv$ has read-only access to all prior transactions and may
mount any classical attack consistent with these capabilities.

$\Adv$ wins if it produces a transaction $(\Cgp_{\star}, \pi_{\star})$
that the on-chain verifier accepts, and such that
$\Cgp_{\star}$ is not the result of inserting a leaf into $\Cg$
under any opening of a current member's witness. Informally:
$\Adv$ wins if and only if the contract accepts an unauthorised
state change.

Soundness is the negation of this win condition --- no such
$\Adv$ exists, except with negligible probability in the
security parameter.

\section{Definitions}
\label{sec:defs}

We fix a security parameter $\lambda$ implicit in the curve and
hash choices.

\begin{definition}[Group commitment]
A \emph{group commitment} $\Cg \in \Fr$ is the Merkle root of a
binary tree of depth $D$ whose leaves are field elements, hashed
at every internal node by Poseidon2. The membership set has
cardinality at most $2^{D}$.
\end{definition}

\begin{definition}[Merkle path, root computation, verifier]
\label{def:merkle-interface}
A leaf position is an index $\Idx \in \{0, 1, \ldots, 2^{D} - 1\}$.
A \emph{Merkle path} is a sequence $\Pth = (s_1, \ldots, s_{D})$
of sibling values in $\Fr$, one per tree level. The
deterministic \emph{root-computation} function
\[
   \MerkleRoot(\Idx, \ell, \Pth)\;\in\;\Fr
\]
takes the leaf value $\ell$, walks the tree from leaf to root,
and at each level $i$ combines the current node $c$ with sibling
$s_i$ under Poseidon2 according to the $i$-th bit of $\Idx$:
\[
   c \;\mapsto\;
   \begin{cases}
     \Poseidon(c,\ s_i) & \text{if the $i$-th bit of $\Idx$ is $0$,} \\
     \Poseidon(s_i,\ c) & \text{if the $i$-th bit of $\Idx$ is $1$.}
   \end{cases}
\]
The \emph{verifier} is the predicate
\[
   \MerkleVerify(\Cg,\, \Idx,\, \ell,\, \Pth)
   \;\equiv\;
   \bigl[\ \MerkleRoot(\Idx,\, \ell,\, \Pth) \;=\; \Cg\ \bigr].
\]
All later definitions invoke this same indexed interface.
\end{definition}

\begin{definition}[Membership relation $\RMem$]
\label{def:rmem}
The relation
\[
\RMem
= \bigl\{\bigl(\Cg;\; (\Idx, \ell, \Pth)\bigr)
       : \MerkleVerify(\Cg, \Idx, \ell, \Pth) = 1 \bigr\}.
\]
The public input is $\Cg$; the witness $(\Idx, \ell, \Pth)$
asserts that position $\Idx$ in the tree of $\Cg$ holds leaf
value $\ell$.
\end{definition}

\begin{definition}[Group-membership keystone update relation $\RUpd$]
\label{def:rupd}
Fix a sentinel field element $\Empty \in \Fr$ disjoint from the
image of any honest leaf-construction routine the deployment
uses; the deployment instantiates $\Empty$ as a fixed
domain-separated constant. Fix a domain-separation identifier
$\mathsf{tag}_{\RUpd}$ that uniquely names this relation
(distinct from any other circuit deployed under the same SRS;
see \Cref{sec:notes}, ``Domain separation in Fiat--Shamir''). The
relation
\[
\RUpd
= \left\{\bigl(\Cg, \Cgp, e, t;\; w\bigr) :
\begin{aligned}
   &t = \mathsf{tag}_{\RUpd} \\
   &w = (\Idx_a,\, \ell_a,\, \Pth_a,\;
         \Idx_e,\, \ell^{\star},\, \Pth_e) \\
   &\ell_a \ne \Empty \\
   &\ell^{\star} \ne \Empty \\
   &\Idx_a \ne \Idx_e \\
   &\MerkleVerify(\Cg,\, \Idx_a,\, \ell_a,\, \Pth_a) = 1 \\
   &\MerkleVerify(\Cg,\, \Idx_e,\, \Empty,\, \Pth_e) = 1 \\
   &\Cgp \;=\; \MerkleRoot(\Idx_e,\, \ell^{\star},\, \Pth_e)
\end{aligned}\right\}.
\]
The public input is $(\Cg, \Cgp, e, t)$; the witness comprises
the admitter's position $\Idx_a$, leaf $\ell_a$, and sibling
path $\Pth_a$, together with a target empty position $\Idx_e$,
the new leaf $\ell^{\star}$ to be written at that position, and
the sibling path $\Pth_e$ opening $\Idx_e$ to $\Empty$ in $\Cg$.
The new commitment $\Cgp$ is, by construction, the root obtained
by recomputing the Merkle root from $\ell^{\star}$ at position
$\Idx_e$ against the same siblings $\Pth_e$ that opened $\Empty$
to $\Cg$ at that position.

The relation does not constrain the epoch $e$ in the predicate
body; $e$ is a public input bound into the Fiat--Shamir
transcript (see \Cref{sec:notes}), and chain-level state
(\Cref{sec:system}) enforces $e = \mathsf{self.epoch}$ on each
admission, with the stored epoch incremented by exactly one on
success.
\end{definition}

\begin{remark}[Two-witness shape and position binding]
\label{rem:slot}
The two-witness shape of \Cref{def:rupd} is load-bearing for the
contract's plain-reading guarantee. With only the admitter's
witness $(\Idx_a, \ell_a, \Pth_a)$, the relation would permit a
member to recompute a new root from an arbitrary new leaf at
\emph{their own} position $\Idx_a$ --- i.e., to overwrite or
transfer their own slot. Requiring a separate
Merkle witness that $\Pth_e$ opens $\Idx_e$ to $\Empty$, and
forbidding $\Idx_a = \Idx_e$, restricts the relation to genuine
admissions at positions that were previously empty and are
distinct from the admitter's. The corresponding cryptographic
claim --- that the constraint
$\MerkleVerify(\Cg, \Idx_e, \Empty, \Pth_e) = 1$ actually pins
down position $\Idx_e$ in $\Cg$ to the value $\Empty$ --- is
established by the position-binding statement of
\Cref{lem:merkle} (rather than by any uniqueness-of-path
property, which does not hold).
\end{remark}

\begin{remark}[Leaf semantics --- a deliberate scope choice]
\label{rem:leaf-scope}
\Cref{def:rupd} constrains $\ell^{\star}$ only by
$\ell^{\star} \ne \Empty$; it does not require $\ell^{\star}$ to
be of any particular form. This is a deliberate scope choice: the
relation treats any non-empty field element as an admissible
leaf, and \emph{does not} enforce canonical identity-encoding
(e.g., $\ell^{\star} = \Poseidon(\mathsf{identity\_pk},
\mathsf{blinding})$ for an opening the admitter knows) inside
the circuit. A deployment that requires canonical leaf encoding
must either (i)~enforce it externally --- e.g., a client-side
check before the admitter signs the transaction, an off-chain
attestation, or a registry of canonical pre-images --- or
(ii)~compile a richer $\RUpd$ that includes a leaf-encoding
witness. The proof of \Cref{thm:auth} below treats option~(i):
the cryptographic-soundness claim covers what the
\emph{circuit} enforces, and the trust boundary for
canonical-leaf encoding is therefore explicitly outside the
relation. Implementations that require option~(ii) must
re-derive a relation-specific soundness statement.
\end{remark}

\begin{definition}[Authorisation soundness of the keystone contract]
\label{def:auth}
Let $\Pi = (\Setup, \Prove, \Verify)$ be the PLONK proof system
instantiated on the stack of \Cref{sec:system}, and let
$\mathsf{vk}$ be the verifying key for the keystone $\RUpd$
circuit of \Cref{def:rupd}. Let $\Cg$ be the current on-chain commitment and $e =
\mathsf{self.epoch}$ the epoch the chain passes as a public input
at verification time. The contract is \emph{authorisation-sound}
if, for every probabilistic polynomial-time adversary $\Adv$ with
read-only access to every prior accepted proof on the chain,
\[
\Pr\!\left[
\begin{aligned}
&\Verify(\mathsf{vk}, (\Cg, \Cgp_{\star}, e, \mathsf{tag}_{\RUpd}), \pi_{\star}) = 1 \\
&\wedge\; \nexists\, w :\; \bigl(\Cg, \Cgp_{\star}, e, \mathsf{tag}_{\RUpd}; w\bigr) \in \RUpd
\end{aligned}
\;:\; (\Cgp_{\star}, \pi_{\star}) \leftarrow \Adv
\right] \le \negl(\lambda).
\]
The clause ``read-only access to every prior accepted proof'' is
the chain-deployment quantifier that distinguishes \emph{simulation
extraction} from plain knowledge extraction (\Cref{lem:plonk-se}):
the adversary observes a polynomial history of accepted proofs
before producing $(\Cgp_{\star}, \pi_{\star})$, and the
soundness reduction must rule out malleation of those prior
proofs into a fresh forgery.
\end{definition}

\section{Layer-by-layer reductions}
\label{sec:reductions}

We now state the four reductions that compose into
\Cref{def:auth}. Each is a standard result from the literature;
we recall it in the form that the composition consumes.

\begin{assumption}[$d$-SBDH on BLS12-381]
\label{ass:sbdh}
For every probabilistic polynomial-time adversary $\Adv$ and
every $d = \mathsf{poly}(\lambda)$,
\[
\Pr\!\left[ \Adv\bigl(\{[\tau^i]_1, [\tau^i]_2\}_{i=0}^{d}\bigr)
            = \bigl(c, [1/(\tau - c)]_1\bigr) \right]
\le \negl(\lambda),
\]
where $\tau$ is uniform in $\Fr$ and $c \in \Fr$ is chosen by $\Adv$.
\end{assumption}

\begin{lemma}[KZG binding from $d$-SBDH~\cite{kate-2010-kzg}]
\label{lem:kzg}
Under \Cref{ass:sbdh}, the KZG commitment scheme is binding:
for every probabilistic polynomial-time adversary $\Adv$,
\[
\Pr\!\left[
\begin{aligned}
&\Verify\bigl([f]_1, z, v_1, \pi_1\bigr) = 1 \\
&\wedge\; \Verify\bigl([f]_1, z, v_2, \pi_2\bigr) = 1 \\
&\wedge\; v_1 \ne v_2
\end{aligned}
\;:\; \bigl([f]_1, z, v_1, v_2, \pi_1, \pi_2\bigr) \leftarrow \Adv(\mathrm{SRS})
\right] \le \negl(\lambda).
\]
\end{lemma}

\begin{proof}[Proof sketch]
Standard. An adversary that produces two openings $v_1 \ne v_2$
of the same commitment at the same point $z$ implicitly commits
to two distinct polynomials $f_1, f_2$ with $f_1(z) = v_1$ and
$f_2(z) = v_2$; subtracting yields a non-zero polynomial that
vanishes nowhere on the SRS support, contradicting
\Cref{ass:sbdh}. See~\cite{kate-2010-kzg} for the original
treatment.
\end{proof}

\begin{assumption}[Poseidon2 collision resistance]
\label{ass:p2cr}
The Poseidon2 permutation, instantiated with the canonical
parameter set ($t=3$, $\alpha=5$, $R_F=8$, $R_P=56$, published
round constants and MDS matrix), is collision-resistant in the
sponge mode against probabilistic polynomial-time adversaries.
\end{assumption}

\begin{remark}
\Cref{ass:p2cr} is supported by the published cryptanalysis at the
chosen round counts~\cite{grassi-2023-poseidon2,grassi-2021-poseidon}
against algebraic, Gröbner-basis, interpolation, and higher-order
differential families, with the round count adjusted twice since
the original 2021 publication.
\end{remark}

\begin{lemma}[Position-binding Merkle soundness from
\Cref{ass:p2cr}~\cite{merkle-1989-tree}]
\label{lem:merkle}
Let $\Cg \in \Fr$ be a fixed Merkle root of depth $D$. For every
probabilistic polynomial-time adversary $\Adv$ and every fixed
position $\Idx \in \{0,1,\ldots,2^{D}-1\}$,
\[
\Pr\!\left[
\begin{aligned}
&\MerkleVerify(\Cg,\, \Idx,\, \ell_1,\, \Pth_1) = 1 \\
&\wedge\; \MerkleVerify(\Cg,\, \Idx,\, \ell_2,\, \Pth_2) = 1 \\
&\wedge\; \ell_1 \ne \ell_2
\end{aligned}
\;:\;
\bigl(\ell_1, \Pth_1, \ell_2, \Pth_2\bigr) \leftarrow \Adv(\Cg, \Idx)
\right] \le \negl(\lambda).
\]
That is: a fixed pair $(\Cg, \Idx)$ pins down at most one leaf
value $\ell$ for which any path verifies, up to negligible
probability.
\end{lemma}

\begin{proof}[Proof sketch]
Suppose $\Adv$ outputs $(\ell_1, \Pth_1, \ell_2, \Pth_2)$
satisfying the event. Both
$\MerkleRoot(\Idx, \ell_1, \Pth_1)$ and
$\MerkleRoot(\Idx, \ell_2, \Pth_2)$ equal $\Cg$. Walking up from
the leaf along the bits of $\Idx$, since $\ell_1 \ne \ell_2$, the
two computations begin at different node values at level $0$. At
the lowest level where the two computations \emph{coincide} (which
must exist, since both reach the same final root $\Cg$), the two
preceding Poseidon2 invocations took different inputs but produced
the same output --- a Poseidon2 collision, contradicting
\Cref{ass:p2cr}.
\end{proof}

\begin{remark}[What this lemma does \emph{not} say]
\label{rem:merkle-scope}
\Cref{lem:merkle} does \emph{not} say that two distinct Merkle
paths cannot both verify against the same root. Two genuinely
different leaves (at different positions) both verify against the
same root by construction; the lemma constrains only what happens
at a \emph{fixed} position. The proof of \Cref{thm:auth} relies
exclusively on this position-binding form.
\end{remark}

\begin{assumption}[Poseidon2 as a random oracle in the transcript]
\label{ass:p2rom}
For the purposes of Fiat--Shamir analysis, Poseidon2 invocations
on transcript inputs are modelled as queries to a random oracle.
\end{assumption}

\begin{lemma}[Fiat--Shamir soundness for PLONK~\cite{don-2019-fiat-shamir}]
\label{lem:fs}
Let $\Pi^{\mathsf{int}}$ be the underlying public-coin
interactive PLONK protocol, with knowledge-soundness loss
$\epsilon_{\mathsf{int}}$ against malicious provers. Under
\Cref{ass:p2rom}, the Fiat--Shamir-transformed protocol $\Pi$ has
knowledge soundness with loss
$\epsilon_{\Pi} = \epsilon_{\mathsf{int}} \cdot \mathsf{poly}(q, k)$,
where $q$ is the prover's oracle-query budget and $k$ is the
number of rounds.
\end{lemma}

\begin{proof}[Proof sketch]
Direct application of the multi-round analysis
of~\cite{don-2019-fiat-shamir}, which generalises the earlier
single-round Fiat--Shamir analysis to the round structure used by
the PLONK family. The constants depend on the round count and
the absorption schedule; for $k$ in the range used by PLONK
(roughly three to five rounds, depending on variant), the loss
remains polynomial.
\end{proof}

\begin{lemma}[Simulation-extractable knowledge soundness for the
deployed PLONK variant%
~\cite{gabizon-2019-plonk,ganesh-2022-simext-plonk}]
\label{lem:plonk-se}
Let $\Pi$ be the PLONK proof system of~\cite{gabizon-2019-plonk}
instantiated with the precise Fiat--Shamir transcript discipline
required by~\cite{ganesh-2022-simext-plonk}, namely:
\begin{enumerate}[label=(\roman*),leftmargin=2em]
  \item the transcript is opened by a relation-specific domain
    separator that uniquely identifies the relation, the
    verifying-key digest, and any tier-index parameter
    (\Cref{sec:notes}, ``Domain separation in Fiat--Shamir'');
  \item every public input is absorbed into the transcript
    \emph{before} any verifier challenge is drawn from the
    transcript-so-far (\Cref{sec:notes}, ``Public-input
    absorption order'');
  \item every prover commitment $[a]_1, [b]_1, [c]_1, [z]_1,
    [t]_1$ is absorbed before the immediately following
    challenge is drawn, in the absorption order analysed
    in~\cite{ganesh-2022-simext-plonk};
  \item challenges are drawn by squeezing the transcript hash
    with no further inputs, in the exact order analysed in
    \cite{ganesh-2022-simext-plonk}.
\end{enumerate}

Under \Cref{ass:sbdh} (which implies \Cref{lem:kzg}) and
\Cref{lem:fs}, in the algebraic group model, $\Pi$ satisfies
\emph{simulation-extractable knowledge soundness} as defined
in~\cite{ganesh-2022-simext-plonk}: for every probabilistic
polynomial-time adversary $\Adv$ that interacts with the prover
oracle of $\Pi$ for an adversarially-chosen sequence of
statements and may observe the resulting accepting proofs, and
that subsequently outputs an accepting proof $\pi_{\star}$ on a
\emph{fresh} statement $x_{\star}$ not equal to any earlier
queried statement, there exists a probabilistic polynomial-time
extractor $\mathcal{E}^{\Adv}$ that --- given $\Adv$'s code and
random tape --- outputs a witness $w$ such that $(x_{\star}; w)$
satisfies the circuit, with extraction loss polynomial in $\Adv$'s
running time and total oracle-query budget.
\end{lemma}

\begin{remark}[Scope of the lemma]
\label{rem:se-scope}
\Cref{lem:plonk-se} is not a claim that ``PLONK is simulation
extractable'' as a generic property of the proof system. It is a
claim about the \emph{specific} PLONK variant analysed
in~\cite{ganesh-2022-simext-plonk}, instantiated with exactly the
transcript discipline (i)--(iv) above. Departures from that
discipline --- a different absorption order, an additional
prover message folded into a challenge derivation, a stripped
domain separator, an alternate proof structure such as Plonkup
or HyperPlonk --- void the cited reduction unless re-analysed.
The deployment must therefore pin the prover and verifier to the
analysed transcript; the Fiat--Shamir details are part of the
trusted computing base.
\end{remark}

\begin{remark}[Why plain knowledge soundness does not suffice]
\label{rem:se-vs-ks}
Plain knowledge soundness~\cite{gabizon-2019-plonk} only
guarantees that an isolated adversary producing an accepting
proof has a witness in the extractor's view. In a deployed
on-chain setting, the adversary observes a polynomial number of
prior accepting proofs published by the chain (whether produced
honestly by other clients or by earlier adversarial submissions
that the chain accepted). Plain knowledge soundness does not
rule out that such an adversary can malleate one or more of the
observed proofs into a fresh accepting proof on a \emph{different}
statement without learning a witness. The simulation-extractable
strengthening of~\cite{ganesh-2022-simext-plonk} is precisely the
notion that closes this gap: it covers adversaries that observe
prior accepting proofs --- regardless of whether those proofs
were generated honestly or adversarially --- and asserts that
no fresh accepting proof on a new statement can be produced
without an extractable witness.
\end{remark}

\begin{remark}[AGM heuristic and variant pinning]
\label{rem:agm}
The algebraic group model is a heuristic restriction on
$\Adv$'s strategies rather than a standard-model assumption; we
flag it explicitly here. A separation between the AGM and the
generic group model could in principle invalidate
\Cref{lem:plonk-se}, although no such separation is currently
known that would apply to the structures used by PLONK. The
deployment is pinned to the specific PLONK variant
of~\cite{gabizon-2019-plonk} plus the simulation-extractability
modifications of~\cite{ganesh-2022-simext-plonk}; substituting a
different variant --- or even reordering the transcript --- voids
\Cref{lem:plonk-se} until the substitution is re-analysed.
\end{remark}

\section{Composition theorem}
\label{sec:theorem}

\begin{theorem}[Authorisation soundness of the keystone contract]
\label{thm:auth}
Under \Cref{ass:sbdh}, \Cref{ass:p2cr}, and \Cref{ass:p2rom}, and
in the algebraic group model, the group-membership keystone
contract is authorisation-sound in the sense of \Cref{def:auth}.
\end{theorem}

\begin{proof}[Proof sketch]
Fix a PPT adversary $\Adv$ that wins the
authorisation-soundness game with non-negligible probability
$\varepsilon$. By definition (\Cref{def:auth}), $\Adv$ has
read-only access to every prior accepting proof published on
the chain, and outputs $(\Cgp_{\star}, \pi_{\star})$ such that
$\Verify(\mathsf{vk},
(\Cg, \Cgp_{\star}, e, \mathsf{tag}_{\RUpd}), \pi_{\star}) = 1$
and no witness for that statement exists in
$\RUpd$.

The simulation-extractable knowledge soundness of
\Cref{lem:plonk-se} applies directly: an extractor
$\mathcal{E}^{\Adv}$ produces, with probability at least
$\varepsilon - \negl(\lambda)$, a witness
$w_{\star} = (\Idx_a, \ell_a, \Pth_a,\; \Idx_e, \ell^{\star},
\Pth_e)$ such that
$(\Cg, \Cgp_{\star}, e, \mathsf{tag}_{\RUpd}; w_{\star})
\in \RUpd$. The lemma's quantification covers
adversaries that observe arbitrary prior accepting proofs ---
whether produced honestly or by earlier adversarial submissions
the chain accepted --- and rules out malleation of those proofs
into a fresh accepting proof on a new statement
(\Cref{rem:se-vs-ks}). We do not need to invoke zero-knowledge
or to model the chain history as a simulator oracle: the
extractor's existence in \Cref{lem:plonk-se} already accounts
for adversaries that observe the full chain history.

The predicate of $\RUpd$ then gives:
\begin{enumerate}
\item $\ell_a \ne \Empty$ and
  $\MerkleVerify(\Cg, \Idx_a, \ell_a, \Pth_a) = 1$. By
  \Cref{lem:merkle} (position binding), the value committed at
  position $\Idx_a$ in $\Cg$ is uniquely determined up to
  negligible probability, and that value is $\ell_a \ne \Empty$.
  Hence position $\Idx_a$ in $\Cg$ holds a real (non-empty) leaf:
  the admitter is a current member.
\item $\MerkleVerify(\Cg, \Idx_e, \Empty, \Pth_e) = 1$. By the
  same lemma, the value committed at position $\Idx_e$ in $\Cg$
  is $\Empty$ up to negligible probability --- i.e., position
  $\Idx_e$ was previously empty.
\item $\Idx_a \ne \Idx_e$. The empty position is not the
  admitter's, so the relation does not collapse into slot
  rotation (\Cref{rem:slot}).
\item $\ell^{\star} \ne \Empty$ and
  $\Cgp_{\star} = \MerkleRoot(\Idx_e, \ell^{\star}, \Pth_e)$.
  Since $\Pth_e$ is the same sequence of sibling values that
  combined with $\Empty$ at position $\Idx_e$ to yield $\Cg$,
  recombining those siblings with $\ell^{\star}$ at the same
  position produces the root of the tree obtained from $\Cg$ by
  replacing position $\Idx_e$ alone, leaving every other
  committed position unchanged (these other positions are pinned
  by \Cref{lem:merkle} applied to each).
\end{enumerate}

Therefore $\Cgp_{\star}$ commits to a tree that differs from
$\Cg$ exactly at the previously-empty position $\Idx_e$, where
the new value $\ell^{\star} \ne \Empty$ has been written by a
current member at position $\Idx_a \ne \Idx_e$. This is a
witness to membership of
$(\Cg, \Cgp_{\star}, e, \mathsf{tag}_{\RUpd}; w_{\star})$ in
$\RUpd$ --- contradicting the win condition of
\Cref{def:auth}, which required \emph{no} such witness to exist.

Hence $\varepsilon = \negl(\lambda)$, modulo the polynomial
extraction loss of \Cref{lem:plonk-se} and the negligible
collision-finding losses across the position-binding invocations
of \Cref{lem:merkle} (and the further reductions in
\Cref{lem:fs,lem:kzg}).
\end{proof}

\begin{remark}[Sequential composition over chain history]
\label{rem:seq}
\Cref{def:auth} and the proof above quantify over a single
adversary-produced transaction. Sequential composition over the
chain history follows from the chain's total ordering of
transactions: each accepted transaction updates $\Cg$ and
increments $\mathsf{self.epoch}$, and the next adversary inherits
a freshly updated context. Adversary-controlled scheduling of
many in-flight transactions is reduced to this sequential model
by the chain's mempool / consensus layer, which is outside the
cryptographic scope of this paper.
\end{remark}

\begin{corollary}[Partial portability of the stack-level reductions]
\label{cor:family}
The \emph{stack-level} reductions of \Cref{sec:reductions} ---
\Cref{lem:kzg} (KZG binding), \Cref{lem:merkle}
(position-binding Merkle soundness), \Cref{lem:fs}
(Fiat--Shamir), and \Cref{lem:plonk-se}
(simulation-extractable knowledge soundness for the deployed
PLONK variant) --- apply unchanged to any policy that uses the
same underlying cryptographic stack and the same Fiat--Shamir
transcript discipline.

The \emph{state-transition} portion of the argument
(\Cref{thm:auth}'s enumerated steps 1--4) does \emph{not} carry
over without re-derivation. Richer admission rules introduce
additional in-circuit invariants. Representative examples:
\begin{itemize}[leftmargin=2em]
  \item a \emph{quorum-of-$N$} rule adds an aggregate-signature
    or co-witness predicate and may require nullifiers to
    prevent vote double-counting;
  \item a \emph{fixed founder-set} rule requires founder-set
    membership and a fixed-cardinality check;
  \item a \emph{two-of-two} (or general $k$-of-$n$) co-signature
    rule requires two (or $k$) co-witnesses and an
    anti-double-use constraint;
  \item an \emph{admin-key} rule requires a verifiable
    admin-signature check against a hardcoded public key;
  \item rules that admit \emph{removal}, \emph{rotation}, or
    \emph{role transitions} require revocation invariants and
    consistent role bookkeeping;
  \item rules that promise \emph{identity uniqueness} require
    an in-circuit non-membership witness for $\ell^{\star}$
    against a sparse-Merkle or indexed-Merkle structure.
\end{itemize}
Each such invariant changes the witness shape of $\RUpd$ and
therefore changes the post-extraction reasoning that connects a
satisfying witness to a permitted state transition. A soundness
theorem for any such variant must redo the state-transition
enumeration; the reusable content is the cryptographic stack
beneath, not the predicate-specific analysis above it.
\end{corollary}

\Cref{fig:chain} summarises the chain of reductions visually.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
   node distance=4mm,
   layer/.style={draw,rounded corners=2pt,minimum width=78mm,minimum height=8mm,align=center,font=\small},
   dep/.style={-{Latex[length=2mm]},thick,gray!70},
]
\node[layer,fill=blue!8] (curve) at (0,0)
   {BLS12-381 curve \quad ($d$-SBDH, discrete log on $\Gone$)};
\node[layer,fill=blue!8,above=of curve] (kzg)
   {KZG polynomial commitment \quad (binding, hiding)};
\node[layer,fill=blue!8,above=of kzg] (p2)
   {Poseidon2 hash \quad (collision resistance, ROM in transcript)};
\node[layer,fill=blue!8,above=of p2,minimum width=37mm,xshift=-21mm] (merkle)
   {Merkle tree \quad (path soundness)};
\node[layer,fill=blue!8,above=of p2,minimum width=37mm,xshift=21mm] (fs)
   {Fiat--Shamir \quad (NIZK soundness)};
\node[layer,fill=blue!8,above=24mm of p2] (plonk)
   {PLONK proof system \quad (knowledge soundness, AGM)};
\node[layer,fill=orange!18,above=of plonk] (rupd)
   {$\RUpd$ circuit \quad (keystone predicate satisfied)};
\node[layer,fill=orange!28,above=of rupd] (sep)
   {keystone contract \quad (authorisation soundness)};

\draw[dep] (curve.north) -- (kzg.south);
\draw[dep] (kzg.north) -- (plonk.south);
\draw[dep] (curve.north) to[bend left=40] (p2.west);
\draw[dep] (p2.north -| merkle.south) -- (merkle.south);
\draw[dep] (p2.north -| fs.south) -- (fs.south);
\draw[dep] (merkle.north) -- (plonk.south -| merkle.north);
\draw[dep] (fs.north) -- (plonk.south -| fs.north);
\draw[dep] (plonk.north) -- (rupd.south);
\draw[dep] (rupd.north) -- (sep.south);
\end{tikzpicture}
\caption{Dependency stack. Each arrow is one reduction; the
contract (top) is authorisation-sound iff every layer below
holds. The diagonal arrow from BLS12-381 to Poseidon2 marks that
Poseidon2 is defined over the curve's scalar field $\Fr$; it is
not a soundness reduction but a parameter-set choice.}
\label{fig:chain}
\end{figure}

\section{Post-quantum considerations}
\label{sec:pq}

The base assumptions of \Cref{thm:auth} differ sharply in how
they fare against a cryptographically-relevant quantum computer
(CRQC). We delineate them explicitly because the composition is
only as strong as its weakest assumption.

Shor's algorithm~\cite{shor-1994-quantum} recovers discrete
logarithms in any abelian group in polynomial time on a CRQC,
including the source subgroups $\Gone, \Gtwo$ of BLS12-381. This
collapses \Cref{ass:sbdh}: the SRS becomes a full-knowledge
witness for the adversary, who can extract the trapdoor $\tau$
directly from the elements $[\tau^i]_1, [\tau^i]_2$. KZG
binding follows (\Cref{lem:kzg}), then PLONK knowledge
soundness (\Cref{lem:plonk-se}), then \Cref{thm:auth}. The stack
fails simultaneously at the curve layer.

Grover's algorithm gives a quadratic speedup on generic search,
halving the bit-security of preimage and collision resistance
for hash functions. \Cref{ass:p2cr} and \Cref{ass:p2rom} survive a
CRQC with reduced security margins ($128$-bit classical
collision resistance becomes roughly $64$-bit post-quantum) but
do not collapse; the Merkle and Fiat--Shamir layers
(\Cref{lem:merkle,lem:fs}) inherit this degradation without
losing their qualitative soundness.

\begin{proposition}
Under a CRQC, \Cref{thm:auth} fails through the curve layer
alone: \Cref{ass:sbdh} no longer holds, and the chain of
reductions breaks at \Cref{lem:kzg}. The hash-based layers
above continue to satisfy their respective reductions with
halved bit-security margins, but those reductions are no
longer load-bearing because the consumer
(\Cref{lem:plonk-se}) has already failed.
\end{proposition}

A post-quantum variant of the contract requires substituting the
proof system: a hash-based SNARK (FRI / STARKs) or a lattice-based
SNARK would replace PLONK, KZG, and the trusted-setup
assumption simultaneously. The Merkle commitment, the Poseidon2
hash, and the Fiat--Shamir transcript would be reused with no
qualitative change to \Cref{thm:auth}'s structure --- only the
proof-system reduction would change shape. We do not pursue this
substitution here.

\section{Implementation discipline the proof depends on}
\label{sec:notes}

\Cref{thm:auth} is conditional on several operational practices
that are easy to state and easy to get wrong. We list them
explicitly.

\paragraph{Domain separation in Fiat--Shamir.} The transcript
must open with a context tag binding the relation name, the
verifying-key digest, and any tier-index parameter that
distinguishes circuits. Two circuits sharing the same Poseidon2
instance without distinct tags would let an adversary transplant
a challenge derived in one transcript into another, defeating
the soundness loss of \Cref{lem:fs}.

\paragraph{Public-input absorption order.} Every public input
($\Cg$, $\Cgp$, the epoch, the relation tag $\mathsf{tag}_{\RUpd}$)
must be absorbed into the transcript \emph{before} any verifier
challenge is drawn from it. Missing absorptions admit
proof-malleability attacks in which an adversary rewrites a
public input in flight without invalidating the proof; published
deployment postmortems document the operational cost of getting
this wrong~\cite{don-2019-fiat-shamir}.

\paragraph{SRS provenance.} The reused KZG ceremony output must
be hash-chained into the verifying-key supply chain using a
collision-resistant hash distinct from the in-circuit one
(SHA-256, in the deployment here~\cite{nist-fips-180-4}). The
verifying-key hash binds every published verifier to the exact
SRS bytes produced by the ceremony; otherwise the
one-honest-contributor assumption is not portable to the
verifying side.

\paragraph{Tier choice locked at group creation.} A group's
Merkle depth is fixed at creation time; growing the membership
set past the tier's bound requires migrating to a larger-tier
contract, not patching the deployed one. The proof of
\Cref{thm:auth} treats $D$ as a fixed parameter; a dynamic $D$
would require revisiting \Cref{lem:merkle}.

\paragraph{Predicate scope.} The proof here is for the
keystone's minimum predicate (\Cref{def:rupd}). Richer admission
rules substitute tighter predicates inside $\RUpd$, but the
predicate's content does not enter \Cref{lem:plonk-se} or any
layer below: it appears only in the final reduction step (the
predicate implies the contract's authorisation property).
\Cref{cor:family} therefore applies to any such variant
provided the predicate is correctly compiled and the
compilation is verified against the verifying-key digest --- and
provided the variant's own state-transition argument has been
re-derived.

\paragraph{Identity uniqueness is not enforced by the predicate.}
\Cref{def:rupd} constrains $\ell^{\star}$ to be non-empty but
does not require that $\ell^{\star}$ differ from any leaf already
present in $\Cg$. A current member may therefore admit a value
that already occurs elsewhere in the tree, or two distinct values
that share an underlying identity key (with different blinding
factors). This is intrinsic to the keystone predicate ---
``any current member admits any leaf'' --- and is by construction.
Deployments that require one-identity-per-member must either
enforce uniqueness out-of-band (e.g., via an external nullifier
set) or compile a richer predicate that carries a non-membership
witness for $\ell^{\star}$. The latter requires a sparse-Merkle or
indexed-Merkle variant, since binary Merkle non-membership is not
$O(\log n)$.

\paragraph{Bootstrap is outside the proof scope.}
\Cref{thm:auth} conditions on a non-empty initial commitment
$\Cg$: at least one leaf $\ell_a$ must already be present for any
admission to verify. How that initial leaf is installed --- via a
genesis transaction, a founder signature, or a dedicated
\texttt{create\_group} contract method --- is a separate
authorisation question that this paper does not analyse. A
deployment must publish the bootstrap construction alongside the
soundness statement; ad-hoc initial-root selection by an untrusted
party voids \Cref{thm:auth}.

\paragraph{Verifying-key supply chain.}
The threat model (\Cref{sec:threat}) grants $\Adv$ read-only
access to the deployed verifying keys. \Cref{thm:auth} therefore
conditions on the on-chain $\mathsf{vk}$ being the one produced
by preprocessing the canonical keystone $\RUpd$ circuit under
the Ethereum Foundation KZG SRS. A maliciously-deployed
verifying key that uses an alternative SRS for which the deployer
knows $\tau$ admits proofs that the contract accepts but which
are unsound under the EF SRS.

Trust in the supply chain can be reduced --- though not
eliminated within the scope of this paper --- by the following
deployment-side disciplines, in increasing order of
trust-minimisation:
\begin{enumerate}[label=(\alph*),leftmargin=2em]
  \item \emph{Out-of-band digest publication.} The SHA-256
    digest of $\mathsf{vk}$ is published with the release
    artifact; each user verifies the on-chain $\mathsf{vk}$
    against the published digest. This is the minimum
    discipline and the only one strictly required by the
    cryptographic-soundness statement, but it places the trust
    on each individual user.
  \item \emph{On-chain digest anchoring.} The verifying-key
    digest is committed at contract-deployment time in an
    immutable contract-storage slot (e.g., a release-tag
    constant), and every relevant transaction additionally
    checks $\mathsf{SHA\text{-}256}(\mathsf{vk}) = \mathsf{vk\_digest}$.
    The chain itself then enforces vk integrity; users verify
    only the digest constant, not the vk bytes.
  \item \emph{Immutable verifier registry.} A separate
    on-chain registry contract, deployed once and made
    immutable, maps each canonical $(\text{relation}, \text{tier})$
    pair to the verifying-key digest produced by deterministic
    preprocessing of a published circuit source. Policy
    contracts consult the registry rather than hard-coding
    digests. This isolates the trust assumption to a single
    audited deployment artifact.
  \item \emph{Deterministic deployment-artifact derivation.}
    The verifying key is derived deterministically from
    (the SRS digest, the circuit source digest, the
    preprocessing routine digest). Any party can re-derive
    $\mathsf{vk}$ from public inputs alone and compare digests;
    no trust in a release artifact is required. This is the
    strongest discipline but requires fully reproducible
    builds.
\end{enumerate}
\Cref{thm:auth} is silent on which of (a)--(d) the deployment
chooses; what it requires is only that the on-chain $\mathsf{vk}$
be the canonical one. Tightening the trust statement above the
minimum (a) is a deployment-engineering question outside the
cryptographic scope of this paper, but the choice is
load-bearing for what the deployment can claim end-to-end.

\paragraph{Epoch monotonicity is chain-state, not a circuit
invariant.} \Cref{def:rupd} does not constrain the epoch $e$ in
its predicate body: $e$ is a public input bound into the
Fiat--Shamir transcript --- so an accepted proof attests to a
specific epoch value --- but the predicate itself imposes no
arithmetic relation among epoch values. Monotonicity (each
admission strictly increases $\mathsf{self.epoch}$ by exactly one)
is enforced by the on-chain contract, which passes the current
epoch as the public input and increments stored state on success.
Sequential composition (\Cref{rem:seq}) is therefore conditional
on the chain providing a total ordering of transactions; chain
reorganisations are a chain-level concern and outside the
cryptographic scope.

\section{Conclusion}
\label{sec:conclusion}

We presented a self-contained compositional sketch of the
authorisation-soundness chain for a SNARK-gated group-membership
keystone contract --- the minimum-predicate construction in which
any current member may admit any new leaf at a previously-empty
position of the membership commitment. Each layer of the
cryptographic stack contributes a single reduction; composing
them gives a top-level soundness statement that is fully
auditable against a small set of base assumptions: $d$-SBDH on
BLS12-381, collision resistance of Poseidon2 at its published
parameters, the random-oracle modelling of Poseidon2 inside the
transcript, and the one-honest-contributor assumption of the
reused structured reference string.

Two structural points are load-bearing and easy to miss. First,
the update relation requires \emph{two} Merkle witnesses --- one
for the admitter's membership, one for the target slot's
emptiness, with index distinctness between them. A naive
single-witness relation would permit a current member to overwrite
their own slot rather than genuinely admit a new member; the
two-witness shape rules this out (\Cref{rem:slot}). Second, the
proof-system reduction is the simulation-extractable strengthening
of plain knowledge soundness (\Cref{rem:se-vs-ks}); plain
knowledge soundness is insufficient against an adversary that
observes a polynomial history of accepted proofs on chain. The
strengthening is established for PLONK with updatable SRS under
the Fiat--Shamir absorption discipline catalogued in
\Cref{sec:notes}.

We made explicit which assumption fails first under a CRQC, and
we listed the operational practices the proof is conditional on
--- bootstrap, verifying-key supply chain, and chain-level
sequential composition. The result is a checklist of what must
hold for the deployment to be authorisation-sound, and a precise
statement of the boundary between the part of the stack that
survives Shor and the part that does not.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
